---
title: "Replication studies of Dijkstra & Buunk (1998)"
author: "Thomas Pollet"
date: '`r format(Sys.Date())`'
output:
  html_document:  
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Background for revision.

Following a review, we were asked to revise our paper with regards to the meta-analysis, so note that these are the only substantially changed sections. (Though we did also remove the chunks which exported the results from the Bayes Factor analyses, as broom has deprecated the tidying functions for 'bayes'). 

Note that there accompanying documents relating to the effect size calculations for these meta-analyses. This analysis document will require you to install packages (see 'session info' for packages needed) and have the relevant data files in your folder.

# Study 1

## Data Wrangling

Importing the datasets for entire study. These are as they were on Qualtrics, with the exception of the removal of IP addresses, 'preview' completions, and personal codes allowing withdrawal

```{r}
require(dplyr)
require(skimr)
require(haven)
Data_online<-read_spss("Study1-Online.sav")
Data_field<-read_spss("Study1-Field.sav")
```
 
Q54 is the last question, therefore this indicates completion.

```{r}
Data_online <- Data_online %>% filter(!is.na(Q54))
Data_field <- Data_field %>% filter(!is.na(Q54))
```

Only heterosexual participants included.

```{r}
Data_online<-Data_online %>% filter(Q6==1)
Data_field <- Data_field %>% filter(Q6==1)
```

Age for descriptives.

```{r}
Age<-c(Data_online$Q5,Data_field$Q5)
mean(Age)
sd(Age)
min(Age)
max(Age)
```

Gender for descriptives.

```{r}
Gender<-c(Data_online$Q4,Data_field$Q4)
table(Gender)
prop.table(table(Gender))
```

Student and romantic relationship for descriptives

```{r}
Student<-c(Data_online$Q8,Data_field$Q8)
table(Student)
prop.table(table(Student))
Romantic<-c(Data_online$Q7,Data_field$Q7)
table(Romantic)
prop.table(table(Romantic))
```

## Subset for analysis

```{r}
Data_analysis1<- Data_online %>% select(Q4,Q23:Q37,Q39,Q40,Q41,Q42,Q43,Q44,FL_21_DO_Scenario5_attractiveandnotdominantfemale,FL_21_DO_Scenario7_unattractiveanddominantfemale,FL_21_DO_Scenario6_attractiveanddominantfemale,FL_21_DO_Scenario8_unattractiveandnonedominantfemale,FL_17_DO_Scenario_attractiveandnon_dominantmale,FL_17_DO_Scenario3_dominantandunattractivemale,FL_17_DO_Scenario1_attractiveanddominantmale,FL_17_DO_Scenario4_NotDominantandUnattractivemale, Q93:Q98)
names(Data_analysis1)<-c("Gender","Suspicious","Betrayed","Worried","Distrustful","Jealousy","Rejected","Hurt","Anxious","Angry", "Threatened","Sad","Upset","Attractiveness_check1","Attractiveness_check2","Assertiveness","Self_confidence","Extroverted","Influential","Socially_competent","Good_judge_of_character","Attractive_not_dominant_woman","Unattractive_dominant_woman","Attractive_dominant_woman","Unattractive_not_dominant_woman","Attractive_not_dominant_man","Unattractive_dominant_man","Attractive_dominant_man","Unattractive_not_dominant_man","Mate_value1","Mate_value2", "Mate_value3","Mate_value4", "Mate_value5", "Mate_value6")
Data_analysis1$Sample<-rep("Online",nrow(Data_analysis1))
# For some reason qualtrics exports.The label here but not elsewhere Q34.
Data_analysis2<- Data_field %>% select(Q4,Q23:Q34, Q36:Q37,Q39,Q40,Q41,Q42,Q43,Q44,Q74,Q77,Q83,Q80,Q68,Q71,Q89,Q86, Q93:Q98)
names(Data_analysis2)<-c("Gender","Suspicious","Betrayed","Worried","Distrustful","Jealousy","Rejected","Hurt","Anxious","Angry", "Threatened","Sad","Upset","Attractiveness_check1","Attractiveness_check2","Assertiveness","Self_confidence","Extroverted","Influential","Socially_competent","Good_judge_of_character","Attractive_not_dominant_woman","Unattractive_dominant_woman","Attractive_dominant_woman","Unattractive_not_dominant_woman","Attractive_not_dominant_man","Unattractive_dominant_man","Attractive_dominant_man","Unattractive_not_dominant_man", "Mate_value1","Mate_value2", "Mate_value3","Mate_value4", "Mate_value5", "Mate_value6")
Data_analysis2$Sample<-rep("Field",nrow(Data_analysis2))
Data_analysis<-rbind(Data_analysis1,Data_analysis2)

```

## Recode to get the 2x2 condition variable. 

Using "case_when". Also generate ID

```{r}
Data_analysis<-Data_analysis %>% mutate(Attractive_condition=case_when(Attractive_not_dominant_woman == 1 | Attractive_dominant_woman == 1 | Attractive_not_dominant_man == 1 | Attractive_dominant_man == 1 ~ "Attractive", TRUE ~ "Not Attractive"), Dominant_condition=case_when(Attractive_dominant_woman == 1 | Unattractive_dominant_woman == 1 | Attractive_dominant_man == 1 | Unattractive_dominant_man == 1 ~ "Dominant", TRUE ~ "Not Dominant"), ID=1:nrow(Data_analysis))
write.csv(Data_analysis, "Dataset1.csv", row.names = F)
write_sav(Data_analysis, "Dataset1.sav")
```

## Cronbach's alpha.

```{r}
require(psych)
alpha<- Data_analysis %>% dplyr::select(Mate_value1:Mate_value6)
require(psych)
psych::alpha(as.data.frame(alpha))
```

Sum scale.

```{r}
Data_analysis<-Data_analysis %>% mutate(Mate_value= Mate_value1+Mate_value2+Mate_value3+Mate_value4+Mate_value5+Mate_value6)
```

There was no significant difference between the genders in mate value, therefore there is no value of including mate value as a covariate. Note that there is one missing value.

```{r}
t.test(Mate_value~Gender, data=Data_analysis)
```

```{r}
require(tidyr)
summary_mate_value <- Data_analysis %>% # "Start with the data set
  group_by(Gender) %>% # Then group by IV
  summarize(N = length(na.omit(Mate_value)),
            Mean_mate_value = mean(Mate_value, na.rm=T),
            SD_mate_value = sd(Mate_value,na.rm = T),
            SE_mate_value= SD_mate_value/sqrt(N)) # Then summarize each group, these are complete so we can use same N
summary_mate_value

```

Similar to Dijkstra et al. 1998, there were no significant effects of conditons on mate value. 

```{r}
t.test(Mate_value~Attractive_condition, data=Data_analysis)
t.test(Mate_value~Dominant_condition, data=Data_analysis)
```


## Manipulation checks.

Using the 'ez' package.

```{r}
require(dplyr)
Data_analysis_men<- Data_analysis %>% filter(Gender==1)
Data_analysis_women<- Data_analysis %>% filter(Gender==2)

```


```{r}
require(ez)
require(papaja)
Ez_ANOVA1<-ezANOVA(Data_analysis_men, dv=Attractiveness_check1, wid=ID, between=Attractive_condition*Dominant_condition, detailed=TRUE, type = 3)
Ez_ANOVA1
Ez_ANOVA2<-ezANOVA(Data_analysis_women, dv=Attractiveness_check1, wid=ID, between=Attractive_condition*Dominant_condition, detailed=TRUE, type = 3)
Ez_ANOVA2
Ez_ANOVA3<-ezANOVA(Data_analysis_men, dv=Attractiveness_check2, wid=ID, between=Attractive_condition*Dominant_condition, detailed=TRUE, type = 3)
Ez_ANOVA3
Ez_ANOVA4<-ezANOVA(Data_analysis_women, dv=Attractiveness_check2, wid=ID, between=Attractive_condition*Dominant_condition, detailed=TRUE, type = 3)
Ez_ANOVA4
```

```{r}
require(apa)
anova_apa(Ez_ANOVA1, es="ges", format = "rmarkdown")
anova_apa(Ez_ANOVA2, es="ges", format = "rmarkdown")
anova_apa(Ez_ANOVA3, es="ges", format = "rmarkdown")
anova_apa(Ez_ANOVA4, es="ges", format = "rmarkdown")
```

```{r}
summary_attractive_men <- Data_analysis_men  %>% # "Start with the data set
  group_by(Attractive_condition) %>% # Then group by IV
  summarize(N = length(Attractiveness_check1), # Then summarize each group, these are complete so we can use same N
            Mean_att1 = mean(Attractiveness_check1),
            SD_att1 = sd(Attractiveness_check1),
            SE_att1 = SD_att1/sqrt(N), # Then summarize each group, these are complete so we can use same N
            Mean_att2 = mean(Attractiveness_check2),
            SD_att2 = sd(Attractiveness_check2),
            SE_att2 = SD_att2/sqrt(N)) 
summary_attractive_men

summary_attractive_women <- Data_analysis_women  %>% # "Start with the data set
  group_by(Attractive_condition) %>% # Then group by IV
  summarize(N = length(Attractiveness_check1), # Then summarize each group, these are complete so we can use same N
            Mean_att1 = mean(Attractiveness_check1),
            SD_att1 = sd(Attractiveness_check1),
            SE_att1 = SD_att1/sqrt(N), # Then summarize each group, these are complete so we can use same N
            Mean_att2 = mean(Attractiveness_check2),
            SD_att2 = sd(Attractiveness_check2),
            SE_att2 = SD_att2/sqrt(N)) 
summary_attractive_women

```

MANOVA for dominance (note no checks for assumption tests - these were also not reported in Dijkstra & Buunk, 1998).

```{r}
Manovamodel_men <- manova(cbind(Assertiveness, Self_confidence,Extroverted,Influential,Socially_competent,Good_judge_of_character) ~ Dominant_condition, data = Data_analysis_men)
summary(Manovamodel_men)
summary(Manovamodel_men, test="Roy")
summary(Manovamodel_men, test="Wilks")
summary(Manovamodel_men, test="Hotelling-Lawley")
summary.aov(Manovamodel_men)
```

Following a reviewer's request, we also added attractiveness.

```{r}
Manovamodel_men_attr <- manova(cbind(Assertiveness, Self_confidence,Extroverted,Influential,Socially_competent,Good_judge_of_character) ~ Dominant_condition*Attractive_condition, data = Data_analysis_men)
summary(Manovamodel_men_attr)
summary(Manovamodel_men_attr, test="Roy")
summary(Manovamodel_men_attr, test="Wilks")
summary(Manovamodel_men_attr, test="Hotelling-Lawley")
summary.aov(Manovamodel_men_attr)
Manovamodel_men_attr$coefficients # check signs.
```

Note that there were 3 women who did not complete all items.

```{r}
Manovamodel_women <- manova(cbind(Assertiveness, Self_confidence,Extroverted,Influential,Socially_competent,Good_judge_of_character) ~ Dominant_condition, data = Data_analysis_women)
summary(Manovamodel_women)
summary(Manovamodel_women, test="Roy")
summary(Manovamodel_women, test="Wilks")
summary(Manovamodel_women, test="Hotelling-Lawley")
summary.aov(Manovamodel_women)
```

Following a reviewer's request, we also added attractiveness. Note that the effect is stronger for dominance than it is for attractiveness. In essence it is not surprising that an attractiveness manipulation yields higher ratings in social dominance.

```{r}
Manovamodel_women_attr <- manova(cbind(Assertiveness, Self_confidence,Extroverted,Influential,Socially_competent,Good_judge_of_character) ~ Dominant_condition*Attractive_condition, data = Data_analysis_women)
summary(Manovamodel_women_attr)
summary(Manovamodel_women_attr, test="Roy")
summary(Manovamodel_women_attr, test="Wilks")
summary(Manovamodel_women_attr, test="Hotelling-Lawley")
summary.aov(Manovamodel_women_attr)
Manovamodel_women_attr$coefficients # check signs.
```

## Hypothesis tests

```{r}
Ez_ANOVA_jealousy<-ezANOVA(Data_analysis, dv=Jealousy, wid=ID, between=.(Attractive_condition,Dominant_condition,Gender), detailed=TRUE, type=3)
Ez_ANOVA_jealousy
anova_apa(Ez_ANOVA_jealousy, es="ges", format = "rmarkdown")
```

Same conclusion.

```{r}
require(dplyr)
Data_analysis_covar<- Data_analysis %>% filter(!is.na(Mate_value))
Ez_ANOVA_jealousy_covar<-ezANOVA(Data_analysis_covar, dv=Jealousy, wid=ID, between=.(Attractive_condition,Dominant_condition,Gender), between_covariates = Mate_value, detailed=TRUE, type=3)
Ez_ANOVA_jealousy_covar
anova_apa(Ez_ANOVA_jealousy_covar, es="ges", format = "rmarkdown")
```


```{r}
Ez_ANOVA_jealousy_men<-ezANOVA(Data_analysis_men, dv=Jealousy, wid=ID, between=Attractive_condition*Dominant_condition, detailed=TRUE, type=3)
Ez_ANOVA_jealousy_men
Ez_ANOVA_jealousy_women<-ezANOVA(Data_analysis_women, dv=Jealousy, wid=ID, between=Attractive_condition*Dominant_condition, detailed=TRUE, type=3)
Ez_ANOVA_jealousy_women
anova_apa(Ez_ANOVA_jealousy_men, es="ges", format = "rmarkdown")
anova_apa(Ez_ANOVA_jealousy_women, es="ges", format = "rmarkdown")
```

Means and SD.

```{r}
summary_jealousy_attractiveness_men <- Data_analysis_men  %>% # "Start with the data set
  group_by(Attractive_condition) %>% # Then group by IV
  summarize(N = length(Jealousy), # Then summarize each group, these are complete so we can use same N
            Mean_jeal = mean(Jealousy),
            SD_jeal = sd(Jealousy),
            SE_jeal = SD_jeal/sqrt(N)) # Then summarize each group, these are complete so we can use same N
summary_jealousy_attractiveness_men

summary_jealousy_attractiveness_women <- Data_analysis_women  %>% # "Start with the data set
  group_by(Attractive_condition) %>% # Then group by IV
  summarize(N = length(Jealousy), # Then summarize each group, these are complete so we can use same N
            Mean_jeal = mean(Jealousy),
            SD_jeal = sd(Jealousy),
            SE_jeal = SD_jeal/sqrt(N)) # Then summarize each group, these are complete so we can use same N
summary_jealousy_attractiveness_women
```

```{r}
summary_jealousy_dominant_men <- Data_analysis_men  %>% # "Start with the data set
  group_by(Dominant_condition) %>% # Then group by IV
  summarize(N = length(Jealousy), # Then summarize each group, these are complete so we can use same N
            Mean_jeal = mean(Jealousy),
            SD_jeal = sd(Jealousy),
            SE_jeal = SD_jeal/sqrt(N)) # Then summarize each group, these are complete so we can use same N
summary_jealousy_dominant_men

summary_jealousy_dominant_women <- Data_analysis_women  %>% # "Start with the data set
  group_by(Dominant_condition) %>% # Then group by IV
  summarize(N = length(Jealousy), # Then summarize each group, these are complete so we can use same N
            Mean_jeal = mean(Jealousy),
            SD_jeal = sd(Jealousy),
            SE_jeal = SD_jeal/sqrt(N)) # Then summarize each group, these are complete so we can use same N
summary_jealousy_dominant_women
```

## Figures

Men.

```{r}
require(ggplot2)
require(ggthemes)
require(scales)
graph_data_men <- describeBy(Data_analysis_men$Jealousy,list(as.factor(Data_analysis_men$Attractive_condition),as.factor(Data_analysis_men$Dominant_condition)), mat=TRUE,digits=2)

graph_data_women <- describeBy(Data_analysis_women$Jealousy,list(as.factor(Data_analysis_women$Attractive_condition),as.factor(Data_analysis_women$Dominant_condition)), mat=TRUE,digits=2)

names(graph_data_men)[names(graph_data_men) == 'group1'] = 'Attractiveness'
names(graph_data_men)[names(graph_data_men) == 'group2'] = 'Dominance'  
names(graph_data_women)[names(graph_data_women) == 'group1'] = 'Attractiveness'
names(graph_data_women)[names(graph_data_women) == 'group2'] = 'Dominance'  

limits = aes(ymax = mean + sd, ymin=mean - sd)
dodge = position_dodge(width=0.9)
graph_men_bar<-ggplot(graph_data_men, aes(x = Attractiveness, y = mean, fill = Dominance))+
  geom_bar(stat='identity', position=dodge)+
  geom_errorbar(limits, position=dodge, width=0.25) + xlab("Attractiveness condition")+ ylab("Mean Jealousy") + labs(fill="Dominance condition") + theme_tufte(10) + scale_fill_grey(start=.4) + coord_cartesian(ylim=c(1,5))
graph_men_bar
# Reference set
reference_men_mean<-c(3.15,3,3.39,2.44)
reference_men_SD<-c(1.16,1.25,.85,.98)
Attractiveness<-c("Attractive","Attractive","Not Attractive", "Not Attractive")
Dominance<-c("Dominant","Not Dominant","Dominant", "Not Dominant")
reference_men<-cbind.data.frame(reference_men_mean,reference_men_SD,Attractiveness,Dominance)
limits = aes(ymax = reference_men_mean + reference_men_SD, ymin=reference_men_mean - reference_men_SD)
dodge = position_dodge(width=0.9)

graph_men_reference<-ggplot(reference_men, aes(x = Attractiveness, y = reference_men_mean, fill = Dominance))+
  geom_bar(stat='identity', position=dodge)+ 
  geom_errorbar(limits, position=dodge, width=0.25) + xlab("Attractiveness condition")+ ylab("Mean Jealousy") + labs(fill="Dominance condition") + theme_tufte(10) + scale_fill_grey(start=.4) + coord_cartesian(ylim=c(1,5))
graph_men_reference
require(cowplot)
plot_grid(graph_men_bar, graph_men_reference, labels = c("A","B"), hjust = -8, label_size = 8,  ncol = 1, align = 'v')
ggsave("barplot_men.png")
ggsave("barplot_men.pdf")
```

Women

```{r}
require(ggplot2)
require(ggthemes)
require(scales)
graph_data_women <- describeBy(Data_analysis_women$Jealousy,list(as.factor(Data_analysis_women$Attractive_condition),as.factor(Data_analysis_women$Dominant_condition)), mat=TRUE,digits=2)

graph_data_women <- describeBy(Data_analysis_women$Jealousy,list(as.factor(Data_analysis_women$Attractive_condition),as.factor(Data_analysis_women$Dominant_condition)), mat=TRUE,digits=2)

names(graph_data_women)[names(graph_data_women) == 'group1'] = 'Attractiveness'
names(graph_data_women)[names(graph_data_women) == 'group2'] = 'Dominance'  
names(graph_data_women)[names(graph_data_women) == 'group1'] = 'Attractiveness'
names(graph_data_women)[names(graph_data_women) == 'group2'] = 'Dominance'  

limits = aes(ymax = mean + sd, ymin=mean - sd)
dodge = position_dodge(width=0.9)
graph_women_bar<-ggplot(graph_data_women, aes(x = Attractiveness, y = mean, fill = Dominance))+
  geom_bar(stat='identity', position=dodge)+
  geom_errorbar(limits, position=dodge, width=0.25) + xlab("Attractiveness condition")+ ylab("Mean Jealousy") + labs(fill="Dominance condition") + theme_tufte(10) + scale_fill_grey(start=.4) + coord_cartesian(ylim=c(1,5))
graph_women_bar
# Reference set
reference_women_mean<-c(3.62,3.48,2.47,2.83)
reference_women_SD<-c(1.12,1.12,1.07,1.34)
Attractiveness<-c("Attractive","Attractive","Not Attractive", "Not Attractive")
Dominance<-c("Dominant","Not Dominant","Dominant", "Not Dominant")
reference_women<-cbind.data.frame(reference_women_mean,reference_women_SD,Attractiveness,Dominance)
limits = aes(ymax = reference_women_mean + reference_women_SD, ymin=reference_women_mean - reference_women_SD)
dodge = position_dodge(width=0.9)

graph_women_reference<-ggplot(reference_women, aes(x = Attractiveness, y = reference_women_mean, fill = Dominance))+
  geom_bar(stat='identity', position=dodge)+ 
  geom_errorbar(limits, position=dodge, width=0.25) + xlab("Attractiveness condition")+ ylab("Mean Jealousy") + labs(fill="Dominance condition") + theme_tufte(10) + scale_fill_grey(start=.4) + coord_cartesian(ylim=c(1,5))
graph_women_reference
require(cowplot)
plot_grid(graph_women_bar, graph_women_reference, labels = c("A","B"), hjust = -8, label_size = 8,  ncol = 1, align = 'v')
ggsave("barplot_women.png")
ggsave("barplot_women.pdf")
```


### Violin plot

This violin plot looks a bit hideous. That is why we opted for the histogram.

```{r}

Data_analysis$Gender<-as.factor(Data_analysis$Gender)
levels(Data_analysis$Gender) <- c("Men", "Women")
dodge <- position_dodge(width = 0.7)
violinplot<-ggplot(Data_analysis, aes(x = Attractive_condition, y = Jealousy, fill=Dominant_condition)) + geom_violin(position=dodge) + geom_boxplot(position=dodge,width = 0.1, outlier.colour=NA) + xlab("Attractiveness condition")+ ylab("Jealousy") + labs(fill="Dominance condition") + theme(legend.position = "top") + facet_grid(~Gender) + scale_fill_grey(start=.4) + theme_tufte(12)
violinplot
ggsave("violinplot.png", width= 200, height=200, units="mm")
```

```{r}
histogram_men<-ggplot(Data_analysis_men, aes(x=Jealousy)) 
histogram_men <- histogram_men + geom_histogram(binwidth=.5, colour="black", fill="white") + facet_grid(Attractive_condition~Dominant_condition) + theme_tufte(7.5)

histogram_women<-ggplot(Data_analysis_women, aes(x=Jealousy)) 
histogram_women <- histogram_women + geom_histogram(binwidth=.5, colour="black", fill="white") + facet_grid(Attractive_condition~Dominant_condition) + theme_tufte(7.5)

plot_grid(histogram_men, histogram_women, labels = c("Men (N=114)","Women (N=225)"), label_size = 7,  ncol = 1, align = 'v')
ggsave("histogram.png")
ggsave("histogram.pdf")
```



## Additional analyses.

```{r}
require(coin)
require(BayesFactor)
Data_analysis$Attractive_condition<-as.factor(Data_analysis$Attractive_condition)
Data_analysis$Dominant_condition<-as.factor(Data_analysis$Dominant_condition)
Data_analysis$Gender<-as.factor(Data_analysis$Gender)
bf_jealousy <- anovaBF(Jealousy ~ Attractive_condition*Dominant_condition*Gender, data=as.data.frame(Data_analysis))
bf_jealousy
1/bf_jealousy 
independence_test(Jealousy ~ Attractive_condition*Dominant_condition*Gender, data=Data_analysis)
```



The independence test is not significant (but _p_ =.06 in independence test for men). 

```{r}
require(coin)
require(BayesFactor)
Data_analysis_men$Attractive_condition<-as.factor(Data_analysis_men$Attractive_condition)
Data_analysis_men$Dominant_condition<-as.factor(Data_analysis_men$Dominant_condition)
bf_jealousy_men <- anovaBF(Jealousy ~ Attractive_condition*Dominant_condition, data=as.data.frame(Data_analysis_men))
bf_jealousy_men
1/bf_jealousy_men 
independence_test(Jealousy ~ Attractive_condition*Dominant_condition, data=Data_analysis_men)
Data_analysis_women$Attractive_condition<-as.factor(Data_analysis_women$Attractive_condition)
Data_analysis_women$Dominant_condition<-as.factor(Data_analysis_women$Dominant_condition)
bf_jealousy_women <- anovaBF(Jealousy ~ Attractive_condition*Dominant_condition, data=as.data.frame(Data_analysis_women))
bf_jealousy_women
1/bf_jealousy_women # 
independence_test(Jealousy ~ Attractive_condition*Dominant_condition, data=Data_analysis_women)
```



## Bootstrapping.

Note that this will take some time. We cannot specify type of error here.

```{r}
ezBoot1<-ezBoot(Data_analysis_men, dv=Jealousy, wid=ID, between=Attractive_condition*Dominant_condition, resample_within = F, iterations = 1e3)
ezBoot2<-ezBoot(Data_analysis_women, dv=Jealousy, wid=ID, between=Attractive_condition*Dominant_condition, resample_within = F, iterations = 1e3)
```

Plot for bootstrap.

```{r}
p<-ezPlot2(pred=ezBoot1, x= Attractive_condition,split=Dominant_condition)
print(p)
p2<-ezPlot2(pred=ezBoot2, x= Attractive_condition,split=Dominant_condition)
print(p2)
```


## Robustness check for site of collection.

Some of the lower level interaction effects significant but crucially no support for a significant three-way interaction.

```{r}
Ez_ANOVA_jealousy_men_check<-ezANOVA(Data_analysis_men, dv=Jealousy, wid=ID, between=.(Attractive_condition,Dominant_condition,Sample), detailed=TRUE, type=3)
Ez_ANOVA_jealousy_men_check
Ez_ANOVA_jealousy_women_check<-ezANOVA(Data_analysis_women, dv=Jealousy, wid=ID, between=.(Attractive_condition,Dominant_condition,Sample), detailed=TRUE, type=3)
Ez_ANOVA_jealousy_women_check
anova_apa(Ez_ANOVA_jealousy_men_check, es="ges", format = "rmarkdown")
anova_apa(Ez_ANOVA_jealousy_women_check, es="ges", format = "rmarkdown")
```

# Study 2

Note that this overrides some of the code, as it is based on the same code as study 1.

## Data Wrangling

Importing the datasets for entire study. These are as they were on Qualtrics, with the exception of the removal of IP addresses, 'preview' completions, and personal codes allowing withdrawal.

```{r}
require(dplyr)
require(skimr)
require(haven)
Data_online<-read_spss("Study2-Online.sav")
Data_field<-read_spss("Study2-Field.sav")
```
 
Q98 is the last question, therefore this indicates completion.

```{r}
Data_online <- Data_online %>% filter(!is.na(Q98))
Data_field <- Data_field %>% filter(!is.na(Q98))
```

Only heterosexual participants included.

```{r}
Data_online<-Data_online %>% filter(Q6==1)
Data_field <- Data_field %>% filter(Q6==1)
```

Age for descriptives.

```{r}
Age<-c(Data_online$Q5,Data_field$Q5)
mean(Age)
sd(Age)
min(Age)
max(Age)
```

Gender for descriptives.

```{r}
Gender<-c(Data_online$Q4,Data_field$Q4)
table(Gender)
prop.table(table(Gender))
```

Student and romantic relationship for descriptives

```{r}
Student<-c(Data_online$Q8,Data_field$Q8)
table(Student)
prop.table(table(Student))
Romantic<-c(Data_online$Q7,Data_field$Q7)
table(Romantic)
prop.table(table(Romantic))
``` 

## Subset for analysis

```{r}
Data_analysis1<- Data_online %>% select(Q4,Q23:Q37,Q39,Q40,Q41,Q42,Q43,Q44,FL_21_DO_Scenario5_attractiveandnotdominantfemale,FL_21_DO_Scenario7_unattractiveanddominantfemale,FL_21_DO_Scenario6_attractiveanddominantfemale,FL_21_DO_Scenario8_unattractiveandnotdominantfemale,FL_17_DO_Scenario_attractiveandnon_dominantmale,FL_17_DO_Scenario3_dominantandunattractivemale,FL_17_DO_Scenario1_attractiveanddominantmale,FL_17_DO_Scenario4_NotDominantandUnattractivemale, Q93:Q98)
names(Data_analysis1)<-c("Gender","Suspicious","Betrayed","Worried","Distrustful","Jealousy","Rejected","Hurt","Anxious","Angry", "Threatened","Sad","Upset","Attractiveness_check1","Attractiveness_check2","Assertiveness","Self_confidence","Extroverted","Influential","Socially_competent","Good_judge_of_character","Attractive_not_dominant_woman","Unattractive_dominant_woman","Attractive_dominant_woman","Unattractive_not_dominant_woman","Attractive_not_dominant_man","Unattractive_dominant_man","Attractive_dominant_man","Unattractive_not_dominant_man","Mate_value1","Mate_value2", "Mate_value3","Mate_value4", "Mate_value5", "Mate_value6")
Data_analysis1$Sample<-rep("Online",nrow(Data_analysis1))
# For some reason qualtrics exports.The label here but not elsewhere Q34.
Data_analysis2<- Data_field %>% select(Q4,Q23:Q34, Q36:Q37,Q39,Q40,Q41,Q42,Q43,Q44,FL_21_DO_Scenario5_attractiveandnotdominantfemale,FL_21_DO_Scenario7_unattractiveanddominantfemale,FL_21_DO_Scenario6_attractiveanddominantfemale,FL_21_DO_Scenario8_unattractiveandnotdominantfemale,FL_17_DO_Scenario_attractiveandnon_dominantmale,FL_17_DO_Scenario3_dominantandunattractivemale,FL_17_DO_Scenario1_attractiveanddominantmale,FL_17_DO_Scenario4_NotDominantandUnattractivemale, Q93:Q98)
names(Data_analysis2)<-c("Gender","Suspicious","Betrayed","Worried","Distrustful","Jealousy","Rejected","Hurt","Anxious","Angry", "Threatened","Sad","Upset","Attractiveness_check1","Attractiveness_check2","Assertiveness","Self_confidence","Extroverted","Influential","Socially_competent","Good_judge_of_character","Attractive_not_dominant_woman","Unattractive_dominant_woman","Attractive_dominant_woman","Unattractive_not_dominant_woman","Attractive_not_dominant_man","Unattractive_dominant_man","Attractive_dominant_man","Unattractive_not_dominant_man", "Mate_value1","Mate_value2", "Mate_value3","Mate_value4", "Mate_value5", "Mate_value6")
Data_analysis2$Sample<-rep("Field",nrow(Data_analysis2))
Data_analysis<-rbind(Data_analysis1,Data_analysis2)
```

## Recode to get the 2x2 condition variable. 

Using "case_when". Also generate ID

```{r}
Data_analysis<-Data_analysis %>% mutate(Attractive_condition=case_when(Attractive_not_dominant_woman == 1 | Attractive_dominant_woman == 1 | Attractive_not_dominant_man == 1 | Attractive_dominant_man == 1 ~ "Attractive", TRUE ~ "Not Attractive"), Dominant_condition=case_when(Attractive_dominant_woman == 1 | Unattractive_dominant_woman == 1 | Attractive_dominant_man == 1 | Unattractive_dominant_man == 1 ~ "Dominant", TRUE ~ "Not Dominant"), ID=1:nrow(Data_analysis))
write.csv(Data_analysis, "Dataset2.csv", row.names = F)
write_sav(Data_analysis, "Dataset2.sav")
```

## Cronbach's alpha.

```{r}
require(psych)
alpha<- Data_analysis %>% dplyr::select(Mate_value1:Mate_value6)
require(psych)
psych::alpha(as.data.frame(alpha))
```

Sum scale.

```{r}
Data_analysis<-Data_analysis %>% mutate(Mate_value= Mate_value1+Mate_value2+Mate_value3+Mate_value4+Mate_value5+Mate_value6)
```

There was no significant difference between the genders in mate value, therefore there is no value of including mate value as a covariate. Note that there is one missing value.

```{r}
t.test(Mate_value~Gender, data=Data_analysis)
```

```{r}
describeBy(Data_analysis$Mate_value, Data_analysis$Gender)
```


```{r}
library(lsr)
cohensD(Data_analysis$Mate_value~ Data_analysis$Gender)
```
```{r}
library(compute.es)
des(d=.2240383, n.1=178, n.2=277)
```

Similar to Dijkstra et al. 1998, there were no significant effects of conditions on mate value (but _p_=.09 for attractiveness). 

```{r}
t.test(Mate_value~Attractive_condition, data=Data_analysis)
t.test(Mate_value~Dominant_condition, data=Data_analysis)
```

## Manipulation checks.

Using the 'ez' package.

```{r}
require(dplyr)
Data_analysis_men<- Data_analysis %>% filter(Gender==1)
Data_analysis_women<- Data_analysis %>% filter(Gender==2)

```


```{r}
require(ez)
require(papaja)
Ez_ANOVA1<-ezANOVA(Data_analysis_men, dv=Attractiveness_check1, wid=ID, between=Attractive_condition*Dominant_condition, detailed=TRUE, type = 3)
Ez_ANOVA1
Ez_ANOVA2<-ezANOVA(Data_analysis_women, dv=Attractiveness_check1, wid=ID, between=Attractive_condition*Dominant_condition, detailed=TRUE, type = 3)
Ez_ANOVA2
Ez_ANOVA3<-ezANOVA(Data_analysis_men, dv=Attractiveness_check2, wid=ID, between=Attractive_condition*Dominant_condition, detailed=TRUE, type = 3)
Ez_ANOVA3
Ez_ANOVA4<-ezANOVA(Data_analysis_women, dv=Attractiveness_check2, wid=ID, between=Attractive_condition*Dominant_condition, detailed=TRUE, type = 3)
Ez_ANOVA4
```

```{r}
require(apa)
anova_apa(Ez_ANOVA1, es="ges", format = "rmarkdown")
anova_apa(Ez_ANOVA2, es="ges", format = "rmarkdown")
anova_apa(Ez_ANOVA3, es="ges", format = "rmarkdown")
anova_apa(Ez_ANOVA4, es="ges", format = "rmarkdown")
```

```{r}
summary_attractive_men <- Data_analysis_men  %>% # "Start with the data set
  group_by(Attractive_condition) %>% # Then group by IV
  summarize(N = length(Attractiveness_check1), # Then summarize each group, these are complete so we can use same N
            Mean_att1 = mean(Attractiveness_check1),
            SD_att1 = sd(Attractiveness_check1),
            SE_att1 = SD_att1/sqrt(N), # Then summarize each group, these are complete so we can use same N
            Mean_att2 = mean(Attractiveness_check2),
            SD_att2 = sd(Attractiveness_check2),
            SE_att2 = SD_att2/sqrt(N)) 
summary_attractive_men

summary_attractive_women <- Data_analysis_women  %>% # "Start with the data set
  group_by(Attractive_condition) %>% # Then group by IV
  summarize(N = length(Attractiveness_check1), # Then summarize each group, these are complete so we can use same N
            Mean_att1 = mean(Attractiveness_check1),
            SD_att1 = sd(Attractiveness_check1),
            SE_att1 = SD_att1/sqrt(N), # Then summarize each group, these are complete so we can use same N
            Mean_att2 = mean(Attractiveness_check2),
            SD_att2 = sd(Attractiveness_check2),
            SE_att2 = SD_att2/sqrt(N)) 
summary_attractive_women

```

MANOVA for dominance (note no checks for assumption tests, but these have also not been reported in Dijkstra & Buunk, 1998).

```{r}
Manovamodel_men <- manova(cbind(Assertiveness,Self_confidence,Extroverted,Influential,Socially_competent,Good_judge_of_character) ~ Dominant_condition, data = Data_analysis_men)
summary(Manovamodel_men)
summary(Manovamodel_men, test="Roy")
summary(Manovamodel_men, test="Wilks")
summary(Manovamodel_men, test="Hotelling-Lawley")
summary.aov(Manovamodel_men)
```

Following a reviewer's request, we also added attractiveness. 

```{r}
Manovamodel_men_attr <- manova(cbind(Assertiveness,Self_confidence,Extroverted,Influential,Socially_competent,Good_judge_of_character) ~ Dominant_condition*Attractive_condition, data = Data_analysis_men)
summary(Manovamodel_men_attr)
summary(Manovamodel_men_attr, test="Roy")
summary(Manovamodel_men_attr, test="Wilks")
summary(Manovamodel_men_attr, test="Hotelling-Lawley")
summary.aov(Manovamodel_men_attr)
Manovamodel_men_attr$coefficients # check signs.
```

Women.

```{r}
Manovamodel_women <- manova(cbind(Assertiveness,Self_confidence,Extroverted,Influential,Socially_competent,Good_judge_of_character) ~ Dominant_condition, data = Data_analysis_women)
summary(Manovamodel_women)
summary(Manovamodel_women, test="Roy")
summary(Manovamodel_women, test="Wilks")
summary(Manovamodel_women, test="Hotelling-Lawley")
summary.aov(Manovamodel_women)
```

Following a reviewer's request, we also added attractiveness. Note that unlike Study 1, there is no effect of attractiveness in this MANOVA.

```{r}
Manovamodel_women_attr <- manova(cbind(Assertiveness,Self_confidence,Extroverted,Influential,Socially_competent,Good_judge_of_character) ~ Dominant_condition*Attractive_condition, data = Data_analysis_women)
summary(Manovamodel_women_attr)
summary(Manovamodel_women_attr, test="Roy")
summary(Manovamodel_women_attr, test="Wilks")
summary(Manovamodel_women_attr, test="Hotelling-Lawley")
summary.aov(Manovamodel_women_attr)
Manovamodel_women_attr$coefficients # check signs.
```

## Hypothesis tests

```{r}
Ez_ANOVA_jealousy<-ezANOVA(Data_analysis, dv=Jealousy, wid=ID, between=.(Attractive_condition,Dominant_condition,Gender), detailed=TRUE, type=3)
Ez_ANOVA_jealousy
anova_apa(Ez_ANOVA_jealousy, es="ges", format = "rmarkdown")
```

Same conclusion.

```{r}
require(dplyr)
Data_analysis_covar<- Data_analysis %>% filter(!is.na(Mate_value))
Ez_ANOVA_jealousy_covar<-ezANOVA(Data_analysis_covar, dv=Jealousy, wid=ID, between=.(Attractive_condition,Dominant_condition,Gender), between_covariates = Mate_value, detailed=TRUE, type=3)
Ez_ANOVA_jealousy_covar
anova_apa(Ez_ANOVA_jealousy_covar, es="ges", format = "rmarkdown")
```


```{r}
Ez_ANOVA_jealousy_men<-ezANOVA(Data_analysis_men, dv=Jealousy, wid=ID, between=Attractive_condition*Dominant_condition, detailed=TRUE, type=3)
Ez_ANOVA_jealousy_men
Ez_ANOVA_jealousy_women<-ezANOVA(Data_analysis_women, dv=Jealousy, wid=ID, between=Attractive_condition*Dominant_condition, detailed=TRUE, type=3)
Ez_ANOVA_jealousy_women
anova_apa(Ez_ANOVA_jealousy_men, es="ges", format = "rmarkdown")
anova_apa(Ez_ANOVA_jealousy_women, es="ges", format = "rmarkdown")
```

Means and SD.

```{r}
summary_jealousy_attractiveness_men <- Data_analysis_men  %>% # "Start with the data set
  group_by(Attractive_condition) %>% # Then group by IV
  summarize(N = length(Jealousy), # Then summarize each group, these are complete so we can use same N
            Mean_jeal = mean(Jealousy),
            SD_jeal = sd(Jealousy),
            SE_jeal = SD_jeal/sqrt(N)) # Then summarize each group, these are complete so we can use same N
summary_jealousy_attractiveness_men

summary_jealousy_attractiveness_women <- Data_analysis_women  %>% # "Start with the data set
  group_by(Attractive_condition) %>% # Then group by IV
  summarize(N = length(Jealousy), # Then summarize each group, these are complete so we can use same N
            Mean_jeal = mean(Jealousy),
            SD_jeal = sd(Jealousy),
            SE_jeal = SD_jeal/sqrt(N)) # Then summarize each group, these are complete so we can use same N
summary_jealousy_attractiveness_women
```

```{r}
summary_jealousy_dominant_men <- Data_analysis_men  %>% # "Start with the data set
  group_by(Dominant_condition) %>% # Then group by IV
  summarize(N = length(Jealousy), # Then summarize each group, these are complete so we can use same N
            Mean_jeal = mean(Jealousy),
            SD_jeal = sd(Jealousy),
            SE_jeal = SD_jeal/sqrt(N)) # Then summarize each group, these are complete so we can use same N
summary_jealousy_dominant_men

summary_jealousy_dominant_women <- Data_analysis_women  %>% # "Start with the data set
  group_by(Dominant_condition) %>% # Then group by IV
  summarize(N = length(Jealousy), # Then summarize each group, these are complete so we can use same N
            Mean_jeal = mean(Jealousy),
            SD_jeal = sd(Jealousy),
            SE_jeal = SD_jeal/sqrt(N)) # Then summarize each group, these are complete so we can use same N
summary_jealousy_dominant_women
```

## Figures

Men.

```{r}
require(ggplot2)
require(ggthemes)
require(scales)
graph_data_men <- describeBy(Data_analysis_men$Jealousy,list(as.factor(Data_analysis_men$Attractive_condition),as.factor(Data_analysis_men$Dominant_condition)), mat=TRUE,digits=2)

graph_data_women <- describeBy(Data_analysis_women$Jealousy,list(as.factor(Data_analysis_women$Attractive_condition),as.factor(Data_analysis_women$Dominant_condition)), mat=TRUE,digits=2)

names(graph_data_men)[names(graph_data_men) == 'group1'] = 'Attractiveness'
names(graph_data_men)[names(graph_data_men) == 'group2'] = 'Dominance'  
names(graph_data_women)[names(graph_data_women) == 'group1'] = 'Attractiveness'
names(graph_data_women)[names(graph_data_women) == 'group2'] = 'Dominance'  

limits = aes(ymax = mean + sd, ymin=mean - sd)
dodge = position_dodge(width=0.9)
graph_men_bar<-ggplot(graph_data_men, aes(x = Attractiveness, y = mean, fill = Dominance))+
  geom_bar(stat='identity', position=dodge)+
  geom_errorbar(limits, position=dodge, width=0.25) + xlab("Attractiveness condition")+ ylab("Mean Jealousy") + labs(fill="Dominance condition") + theme_tufte(10) + scale_fill_grey(start=.4) + coord_cartesian(ylim=c(1,5))
graph_men_bar
# Reference set
reference_men_mean<-c(3.15,3,3.39,2.44)
reference_men_SD<-c(1.16,1.25,.85,.98)
Attractiveness<-c("Attractive","Attractive","Not Attractive", "Not Attractive")
Dominance<-c("Dominant","Not Dominant","Dominant", "Not Dominant")
reference_men<-cbind.data.frame(reference_men_mean,reference_men_SD,Attractiveness,Dominance)
limits = aes(ymax = reference_men_mean + reference_men_SD, ymin=reference_men_mean - reference_men_SD)
dodge = position_dodge(width=0.9)

graph_men_reference<-ggplot(reference_men, aes(x = Attractiveness, y = reference_men_mean, fill = Dominance))+
  geom_bar(stat='identity', position=dodge)+ 
  geom_errorbar(limits, position=dodge, width=0.25) + xlab("Attractiveness condition")+ ylab("Mean Jealousy") + labs(fill="Dominance condition") + theme_tufte(10) + scale_fill_grey(start=.4) + coord_cartesian(ylim=c(1,5))
graph_men_reference
require(cowplot)
plot_grid(graph_men_bar, graph_men_reference, labels = c("A","B"), hjust = -8, label_size = 8,  ncol = 1, align = 'v')
ggsave("barplot_men_2.png")
ggsave("barplot_men_2.pdf")
```

Women

```{r}
require(ggplot2)
require(ggthemes)
require(scales)
graph_data_women <- describeBy(Data_analysis_women$Jealousy,list(as.factor(Data_analysis_women$Attractive_condition),as.factor(Data_analysis_women$Dominant_condition)), mat=TRUE,digits=2)

graph_data_women <- describeBy(Data_analysis_women$Jealousy,list(as.factor(Data_analysis_women$Attractive_condition),as.factor(Data_analysis_women$Dominant_condition)), mat=TRUE,digits=2)

names(graph_data_women)[names(graph_data_women) == 'group1'] = 'Attractiveness'
names(graph_data_women)[names(graph_data_women) == 'group2'] = 'Dominance'  
names(graph_data_women)[names(graph_data_women) == 'group1'] = 'Attractiveness'
names(graph_data_women)[names(graph_data_women) == 'group2'] = 'Dominance'  

limits = aes(ymax = mean + sd, ymin=mean - sd)
dodge = position_dodge(width=0.9)
graph_women_bar<-ggplot(graph_data_women, aes(x = Attractiveness, y = mean, fill = Dominance))+
  geom_bar(stat='identity', position=dodge)+
  geom_errorbar(limits, position=dodge, width=0.25) + xlab("Attractiveness condition")+ ylab("Mean Jealousy") + labs(fill="Dominance condition") + theme_tufte(10) + scale_fill_grey(start=.4) + coord_cartesian(ylim=c(1,5))
graph_women_bar
# Reference set
reference_women_mean<-c(3.62,3.48,2.47,2.83)
reference_women_SD<-c(1.12,1.12,1.07,1.34)
Attractiveness<-c("Attractive","Attractive","Not Attractive", "Not Attractive")
Dominance<-c("Dominant","Not Dominant","Dominant", "Not Dominant")
reference_women<-cbind.data.frame(reference_women_mean,reference_women_SD,Attractiveness,Dominance)
limits = aes(ymax = reference_women_mean + reference_women_SD, ymin=reference_women_mean - reference_women_SD)
dodge = position_dodge(width=0.9)

graph_women_reference<-ggplot(reference_women, aes(x = Attractiveness, y = reference_women_mean, fill = Dominance))+
  geom_bar(stat='identity', position=dodge)+ 
  geom_errorbar(limits, position=dodge, width=0.25) + xlab("Attractiveness condition")+ ylab("Mean Jealousy") + labs(fill="Dominance condition") + theme_tufte(10) + scale_fill_grey(start=.4) + coord_cartesian(ylim=c(1,5))
graph_women_reference
require(cowplot)
plot_grid(graph_women_bar, graph_women_reference, labels = c("A","B"), hjust = -8, label_size = 8,  ncol = 1, align = 'v')
ggsave("barplot_women_2.png")
ggsave("barplot_women_2.pdf")
```

### Violin plot

This violin plot looks a bit hideous. That is why we opted for the histogram.

```{r}

Data_analysis$Gender<-as.factor(Data_analysis$Gender)
levels(Data_analysis$Gender) <- c("Men", "Women")
dodge <- position_dodge(width = 0.7)
violinplot<-ggplot(Data_analysis, aes(x = Attractive_condition, y = Jealousy, fill=Dominant_condition)) + geom_violin(position=dodge) + geom_boxplot(position=dodge,width = 0.1, outlier.colour=NA) + xlab("Attractiveness condition")+ ylab("Jealousy") + labs(fill="Dominance condition") + theme(legend.position = "top") + facet_grid(~Gender) + scale_fill_grey(start=.4) + theme_tufte(12)
violinplot
ggsave("violinplot_2.png", width= 200, height=200, units="mm")
```

```{r}
histogram_men<-ggplot(Data_analysis_men, aes(x=Jealousy)) 
histogram_men <- histogram_men + geom_histogram(binwidth=.5, colour="black", fill="white") + facet_grid(Attractive_condition~Dominant_condition) + theme_tufte(7.5)

histogram_women<-ggplot(Data_analysis_women, aes(x=Jealousy)) 
histogram_women <- histogram_women + geom_histogram(binwidth=.5, colour="black", fill="white") + facet_grid(Attractive_condition~Dominant_condition) + theme_tufte(7.5)

plot_grid(histogram_men, histogram_women, labels = c("Men (N=178)","Women (N=278)"), label_size = 7,  ncol = 1, align = 'v')
ggsave("histogram_2.png")
ggsave("histogram_2.pdf")
```

### Additional analyses

independence test suggests no effect.

```{r}
require(coin)
require(BayesFactor)
Data_analysis$Attractive_condition<-as.factor(Data_analysis$Attractive_condition)
Data_analysis$Dominant_condition<-as.factor(Data_analysis$Dominant_condition)
Data_analysis$Gender<-as.factor(Data_analysis$Gender)
bf_jealousy <- anovaBF(Jealousy ~ Attractive_condition*Dominant_condition*Gender, data=as.data.frame(Data_analysis))
bf_jealousy
1/bf_jealousy 
independence_test(Jealousy ~ Attractive_condition*Dominant_condition*Gender, data=Data_analysis)
```



```{r}
require(coin)
require(BayesFactor)
Data_analysis_men$Attractive_condition<-as.factor(Data_analysis_men$Attractive_condition)
Data_analysis_men$Dominant_condition<-as.factor(Data_analysis_men$Dominant_condition)
bf_jealousy_men <- anovaBF(Jealousy ~ Attractive_condition*Dominant_condition, data=as.data.frame(Data_analysis_men))
bf_jealousy_men
1/bf_jealousy_men 
independence_test(Jealousy ~ Attractive_condition*Dominant_condition, data=Data_analysis_men)
Data_analysis_women$Attractive_condition<-as.factor(Data_analysis_women$Attractive_condition)
Data_analysis_women$Dominant_condition<-as.factor(Data_analysis_women$Dominant_condition)
bf_jealousy_women <- anovaBF(Jealousy ~ Attractive_condition*Dominant_condition, data=as.data.frame(Data_analysis_women))
bf_jealousy_women
1/bf_jealousy_women # 
independence_test(Jealousy ~ Attractive_condition*Dominant_condition, data=Data_analysis_women)
```



# Meta-analysis (old version).

This was the meta-analysis from a previous version.
We can use the guidance from http://www.stat-help.com/spreadsheets.html to convert everything to a common effect 'r'. Following the recommendation, we can take square root of $\eta^2_p$ to obtain Pearson r. We use the sample sizes as N to provide the weights.

## attractiveness

### Build up a data frame

The original effect size is derived from the _F_-tests, see the accompanying document. 

```{r}
require(esc)
require(metafor)
r_original_att<-sqrt(.0332) # Partial eta squared to r. (Note that this treats partial eta squared as eta squared)
r_att1<-pearsons_r(eta=0.0194012518) # could just use ESC as well
r_att2<-pearsons_r(eta=0.0027411646)
N_original<-152
N_1<-339
N_2<-456
r_i_attract<-c(r_original_att,r_att1,r_att2)
N_i<-c(N_original,N_1,N_2)
Labels<-c("Dijkstra & Buunk 1998: attractiveness*gender (N=152)", "Study 1: attractiveness*gender (N=339)", "Study 2: attractiveness*gender (N=456)")
correlations_1<-cbind.data.frame(r_i_attract, N_i, Labels)
```
Actual analysis
```{r}
require(metafor)
eszcor <- escalc(measure="ZCOR", ri=r_i_attract, ni=N_i, data=correlations_1)
REmodel_attract <-rma(yi=yi, vi=vi, data=eszcor, method="REML", slab=Labels)
REmodel_attract
postscript("forest1.eps",  horizontal = FALSE, onefile = FALSE, paper = "special", height = 12, width = 12)
par(mar=c(5,4,0,6))
forest(REmodel_attract)
dev.off()
```


```{r}
require(bayesmeta)
ma01 <- bayesmeta(y= eszcor[,"yi"], sigma= sqrt(eszcor[,"vi"]), mu.prior.mean = 0, mu.prior.sd = 4,
 tau.prior = function(t){dhalfnormal(t,scale=0.5)})
ma01
forestplot(ma01)
ma01$bayesfactor[1] # Bayes factor
ma01$bayesfactor[2] # minimum bayes factor
```
## Dominance

```{r}
require(esc)
require(metafor)
r_original_dom<-sqrt(.02646373) # Partial eta squared to r. (Note that this treats partial eta squared as eta squared)
r_dom1<-pearsons_r(eta=0.0043368855) # could just use ESC as well
r_dom2<-pearsons_r(eta=0.0003447257)
N_original<-152
N_1<-339
N_2<-456
r_i_dom<-c(r_original_dom,r_dom1,r_dom2)
N_i<-c(N_original,N_1,N_2)
Labels2<-c("Dijkstra & Buunk 1998: dominance*gender (N=152)", "Study 1: dominance*gender (N=339)", "Study 2: dominance*gender (N=456)")
correlations_2<-cbind.data.frame(r_i_dom, N_i, Labels2)
```

```{r}
require(metafor)
eszcor2 <- escalc(measure="ZCOR", ri=r_i_dom, ni=N_i, data=correlations_2)
REmodel_dom <-rma(yi=yi, vi=vi, data=eszcor2, method="REML", slab=Labels2)
REmodel_dom
postscript("forest2.eps",  horizontal = FALSE, onefile = FALSE, paper = "special", height = 12, width = 12)
par(mar=c(5,4,0,6))
forest(REmodel_dom)
dev.off()
```

# Meta-analysis (new version).

Following review, we were asked to conduct a more complete meta-analysis. The spreadsheets provided

As before we can convert everything to a common effect size, Pearson _r_ with N as weights (but note that for those papers relying on a comparison between genders in terms of Pearson correlations, SE was calculated via Fisher's _r_ to Z transformation, this leads to a weighing down of the effect size as here we use that estimate rather than N of the study. This applies to two estimates, and favours the effect). For completeness, we also provide the meta-analysis with and without the transform.

It is also important to bear in mind that the current meta-analyses weighs the effects from an interaction model similarly as those from a main effects model and thus if anything will likely be overoptimistic. Finally, note that the effect size for our studies and the Dijkstra & Buunk paper was calculated in the above sections.

## Attractiveness

```{r}
require(readxl)
attract_meta<-read_excel("meta-analysis_attract.xlsx")
```

```{r}
require(metafor)
eszcor <- escalc(measure="ZCOR", ri=r, ni=N, data=attract_meta)
REmodel_attract_2 <-rma(yi=yi, vi=vi, data=eszcor, method="REML", slab=Label)
REmodel_attract_2
postscript("forest1_new.eps",  horizontal = FALSE, onefile = FALSE, paper = "special", height = 12, width = 12)
par(mar=c(5,4,0,6))
metafor::forest(REmodel_attract_2, addcred=T)
dev.off()
```

No evidence for publication bias. Relatively robust to removals of single studies

```{r}
funnel(REmodel_attract_2)
regtest(REmodel_attract_2)
leave1out(REmodel_attract_2) # leave one out validation.
```

No significant effect of 'Buunk author or not' on unexplained variation in Q. Though one question whether the number of studies suffices.

```{r}
res <- rma(yi, vi, mods = ~Buunk, data=eszcor)
summary(res)
```

```{r}
require(bayesmeta)
ma02 <- bayesmeta(y= eszcor[,"yi"], sigma= sqrt(eszcor[,"vi"]), mu.prior.mean = 0, mu.prior.sd = 4,
 tau.prior = function(t){dhalfnormal(t,scale=0.5)})
ma02
forestplot(ma02)
ma02$bayesfactor[1] # Bayes factor
ma02$bayesfactor[2] # minimum bayes factor
```

### Check if N is used for Fisher's r to Z transform.

**This analysis is reported in the paper**

A minimal shift _r_= .22 with 95% CI = .151 to .297 . This corroborates the above analyses and shows that in this case it does not matter if one uses N derived from Fisher's transform or raw N. As in the end this is more logically consistent. We decided to report these meta-analysis


```{r}
require(readxl)
attract_meta2<-read_excel("meta-analysis_attract-N_marelich.xlsx")
```

```{r}
require(metafor)
eszcor <- escalc(measure="ZCOR", ri=r, ni=N, data=attract_meta2)
REmodel_attract_3 <-rma(yi=yi, vi=vi, data=eszcor, method="REML", slab=Label)
REmodel_attract_3
postscript("forest1_new_m.eps",  horizontal = FALSE, onefile = FALSE, paper = "special", height = 12, width = 12)
par(mar=c(5,4,0,6))
metafor::forest(REmodel_attract_3,alim = c(-1,1), addcred=T)
dev.off()
```

No significant effect of 'Buunk author or not' on unexplained variation in Q.

```{r}
funnel(REmodel_attract_3)
regtest(REmodel_attract_3)
leave1out(REmodel_attract_3) # leave one out validation.
```

```{r}
res <- rma(yi, vi, mods = ~Buunk, data=eszcor)
summary(res)
```

```{r}
require(bayesmeta)
ma03 <- bayesmeta(y= eszcor[,"yi"], sigma= sqrt(eszcor[,"vi"]), mu.prior.mean = 0, mu.prior.sd = 4,
 tau.prior = function(t){dhalfnormal(t,scale=0.5)})
ma03
forestplot(ma03)
ma03$bayesfactor[1] # Bayes factor
ma03$bayesfactor[2] # minimum bayes factor
```

### BRMS Meta-analysis

```{r}
require(brms)
require(brmstools)
eszcor$obs<-1:nrow(eszcor)
model_fisher_attract <- brm(
  yi | se(sqrt(1 / (N - 3))) ~ 1 + (1|obs), 
  data = eszcor, family = gaussian(), 
  prior = c(
    prior(normal(0, 10), "Intercept"),
    prior(student_t(3, 0, 10), "sd")
  ),
  control = list(adapt_delta = 0.95),
  chains = 2, cores = 2, iter = 4000, warmup = 1000
)
```

```{r}
plot(model_fisher_attract)
```

```{r}
pp_check(model_fisher_attract, nsamples = 150)
```

```{r}
summary(model_fisher_attract)
```

```{r}
require(ggthemes)
brms_forest<-brmstools::forest(model_fisher_attract)
brms_forest + scale_x_continuous("Fisher transformed correlation", limits = c(-.8, .8)) + ylab("Study") + 
    theme_tufte()
```

## Dominance 

```{r}
require(readxl)
dominance_meta<-read_excel("meta-analysis_dominance.xlsx")
```

```{r}
require(metafor)
eszcor <- escalc(measure="ZCOR", ri=r, ni=N, data=dominance_meta)
REmodel_dominance_2 <-rma(yi=yi, vi=vi, data=eszcor, method="REML", slab=Label)
REmodel_dominance_2
postscript("forest2_new.eps",  horizontal = FALSE, onefile = FALSE, paper = "special", height = 12, width = 12)
par(mar=c(5,4,0,6))
metafor::forest(REmodel_dominance_2,alim = c(-1,1), addcred=T)
dev.off()
```

```{r}
funnel(REmodel_dominance_2)
regtest(REmodel_dominance_2)
leave1out(REmodel_dominance_2) # leave one out validation.
```

We note that there is substantial heterogeneity but it likely is not sensible at this stage to examine candidate variables for explaining this heterogeneity. (Also note that all but 3 studies do not share Buunk as an author).

### Drop Buunk et al.(2011)

Following a reviewer request we were asked to drop Argentina and Spain from the analysis as the measure could contain 'feminine' aspects. It is already clear from the leave-one-out validation that this will likely not matter for our overall conclusion.

```{r}
dominance_meta_without_Buunk_2011<- dominance_meta %>% slice(-c(4,5)) # These are studies in row 4,5
```

```{r}
require(metafor)
eszcor3 <- escalc(measure="ZCOR", ri=r, ni=N, data=dominance_meta_without_Buunk_2011)
REmodel_dominance_3 <-rma(yi=yi, vi=vi, data=eszcor3, method="REML", slab=Label)
REmodel_dominance_3
postscript("forest3_without_buunk2011.eps",  horizontal = FALSE, onefile = FALSE, paper = "special", height = 12, width = 12)
par(mar=c(5,4,0,6))
metafor::forest(REmodel_dominance_3,alim = c(-1,1), addcred=T)
dev.off()
```

### Bayesian meta-analysis - dominance.


```{r}
require(bayesmeta)
ma04 <- bayesmeta(y= eszcor[,"yi"], sigma= sqrt(eszcor[,"vi"]), mu.prior.mean = 0, mu.prior.sd = 4,
 tau.prior = function(t){dhalfnormal(t,scale=0.5)})
ma04
forestplot(ma04)
ma04$bayesfactor[1] # Bayes factor
ma04$bayesfactor[2] # minimum bayes factor
```

### BRMS Meta-analysis: dominance

```{r}
require(brms)
require(brmstools)
eszcor$obs<-1:nrow(eszcor) # Observation (but label does job)
model_fisher_dom <- brm(
  yi | se(sqrt(1 / (N - 3))) ~ 1 + (1|Label), 
  data = eszcor, family = gaussian(), 
  prior = c(
    prior(normal(0, 10), "Intercept"),
    prior(student_t(3, 0, 10), "sd")
  ),
  control = list(adapt_delta = 0.95),
  chains = 2, cores = 2, iter = 4000, warmup = 1000
)
```

```{r}
plot(model_fisher_dom)
```


```{r}
pp_check(model_fisher_dom, nsamples = 150)
```


```{r}
summary(model_fisher_dom)
```

```{r}
require(ggthemes)
brms_forest<-brmstools::forest(model_fisher_dom)
brms_forest + scale_x_continuous("Fisher transformed correlation", limits = c(-.8, .8)) + ylab("Study") + 
    theme_tufte()
```


# Session info.


```{r}
#/ __| | | |/ __/ __/ _ \/ __/ __|
#\__ \ |_| | (_| (_|  __/\__ \__ \
#|___/\__,_|\___\___\___||___/___/
sessionInfo()
```







