---
title: "Replication studies of Dijkstra & Buunk (1998)"
author: "Thomas Pollet"
date: '`r format(Sys.Date())`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Study 1

## Data Wrangling

Importing the datasets for entire study. These are as they were on Qualtrics, with the exception of the removal of IP addresses, 'preview' completions, and personal codes allowing withdrawal

```{r}
require(dplyr)
require(skimr)
require(haven)
Data_online<-read_spss("Study1-Online.sav")
Data_field<-read_spss("Study1-Field.sav")
```
 
Q54 is the last question, therefore this indicates completion.

```{r}
Data_online <- Data_online %>% filter(!is.na(Q54))
Data_field <- Data_field %>% filter(!is.na(Q54))
```

Only heterosexual participants included.

```{r}
Data_online<-Data_online %>% filter(Q6==1)
Data_field <- Data_field %>% filter(Q6==1)
```

Age for descriptives.

```{r}
Age<-c(Data_online$Q5,Data_field$Q5)
mean(Age)
sd(Age)
min(Age)
max(Age)
```

Gender for descriptives.

```{r}
Gender<-c(Data_online$Q4,Data_field$Q4)
table(Gender)
prop.table(table(Gender))
```

Student and romantic relationship for descriptives

```{r}
Student<-c(Data_online$Q8,Data_field$Q8)
table(Student)
prop.table(table(Student))
Romantic<-c(Data_online$Q7,Data_field$Q7)
table(Romantic)
prop.table(table(Romantic))
```

## Subset for analysis

```{r}
Data_analysis1<- Data_online %>% select(Q4,Q23:Q37,Q39,Q40,Q41,Q42,Q43,Q44,FL_21_DO_Scenario5_attractiveandnotdominantfemale,FL_21_DO_Scenario7_unattractiveanddominantfemale,FL_21_DO_Scenario6_attractiveanddominantfemale,FL_21_DO_Scenario8_unattractiveandnonedominantfemale,FL_17_DO_Scenario_attractiveandnon_dominantmale,FL_17_DO_Scenario3_dominantandunattractivemale,FL_17_DO_Scenario1_attractiveanddominantmale,FL_17_DO_Scenario4_NotDominantandUnattractivemale, Q93:Q98)
names(Data_analysis1)<-c("Gender","Suspicious","Bertrayed","Worried","Distrustful","Jealousy","Rejected","Hurt","Anxious","Angry", "Threatened","Sad","Upset","Attractiveness_check1","Attractiveness_check2","Assertiveness","Self-confidence","Extroverted","Influential","Socially_competent","Good_judge_of_character","Attractive_not_dominant_woman","Unattractive_dominant_woman","Attractive_dominant_woman","Unattractive_not_dominant_woman","Attractive_not_dominant_man","Unattractive_dominant_man","Attractive_dominant_man","Unattractive_not_dominant_man","Mate_value1","Mate_value2", "Mate_value3","Mate_value4", "Mate_value5", "Mate_value6")
Data_analysis1$Sample<-rep("Online",nrow(Data_analysis1))
# For some reason qualtrics exports.The label here but not elsewhere Q34.
Data_analysis2<- Data_field %>% select(Q4,Q23:Q34, Q36:Q37,Q39,Q40,Q41,Q42,Q43,Q44,Q74,Q77,Q83,Q80,Q68,Q71,Q89,Q86, Q93:Q98)
names(Data_analysis2)<-c("Gender","Suspicious","Bertrayed","Worried","Distrustful","Jealousy","Rejected","Hurt","Anxious","Angry", "Threatened","Sad","Upset","Attractiveness_check1","Attractiveness_check2","Assertiveness","Self-confidence","Extroverted","Influential","Socially_competent","Good_judge_of_character","Attractive_not_dominant_woman","Unattractive_dominant_woman","Attractive_dominant_woman","Unattractive_not_dominant_woman","Attractive_not_dominant_man","Unattractive_dominant_man","Attractive_dominant_man","Unattractive_not_dominant_man", "Mate_value1","Mate_value2", "Mate_value3","Mate_value4", "Mate_value5", "Mate_value6")
Data_analysis2$Sample<-rep("Field",nrow(Data_analysis2))
Data_analysis<-rbind(Data_analysis1,Data_analysis2)
```

## Recode to get the 2x2 condition variable. 

Using "case_when". Also generate ID

```{r}
Data_analysis<-Data_analysis %>% mutate(Attractive_condition=case_when(Attractive_not_dominant_woman == 1 | Attractive_dominant_woman == 1 | Attractive_not_dominant_man == 1 | Attractive_dominant_man == 1 ~ "Attractive", TRUE ~ "Not Attractive"), Dominant_condition=case_when(Attractive_dominant_woman == 1 | Unattractive_dominant_woman == 1 | Attractive_dominant_man == 1 | Unattractive_dominant_man == 1 ~ "Dominant", TRUE ~ "Not Dominant"), ID=1:nrow(Data_analysis))
```

## Cronbach's alpha.

```{r}
require(psych)
alpha<- Data_analysis %>% dplyr::select(Mate_value1:Mate_value6)
require(psych)
psych::alpha(as.data.frame(alpha))
```

Sum scale.

```{r}
Data_analysis<-Data_analysis %>% mutate(Mate_value= Mate_value1+Mate_value2+Mate_value3+Mate_value4+Mate_value5+Mate_value6)
```

There was no significant difference between the genders in mate value, therefore there is no value of including mate value as a covariate. Note that there is one missing value.

```{r}
t.test(Mate_value~Gender, data=Data_analysis)
```

```{r}
require(tidyr)
summary_mate_value <- Data_analysis %>% # "Start with the data set
  group_by(Gender) %>% # Then group by IV
  summarize(N = length(na.omit(Mate_value)),
            Mean_mate_value = mean(Mate_value, na.rm=T),
            SD_mate_value = sd(Mate_value,na.rm = T),
            SE_mate_value= SD_mate_value/sqrt(N)) # Then summarize each group, these are complete so we can use same N
summary_mate_value

```

Similar to Dijkstra et al. 1998, there were no significant effects of conditons on mate value. 

```{r}
t.test(Mate_value~Attractive_condition, data=Data_analysis)
t.test(Mate_value~Dominant_condition, data=Data_analysis)
```


## Manipulation checks.

Using the 'ez' package.

```{r}
require(dplyr)
Data_analysis_men<- Data_analysis %>% filter(Gender==1)
Data_analysis_women<- Data_analysis %>% filter(Gender==2)

```


```{r}
require(ez)
require(papaja)
Ez_ANOVA1<-ezANOVA(Data_analysis_men, dv=Attractiveness_check1, wid=ID, between=Attractive_condition*Dominant_condition, detailed=TRUE, type = 3)
Ez_ANOVA1
Ez_ANOVA2<-ezANOVA(Data_analysis_women, dv=Attractiveness_check1, wid=ID, between=Attractive_condition*Dominant_condition, detailed=TRUE, type = 3)
Ez_ANOVA2
Ez_ANOVA3<-ezANOVA(Data_analysis_men, dv=Attractiveness_check2, wid=ID, between=Attractive_condition*Dominant_condition, detailed=TRUE, type = 3)
Ez_ANOVA3
Ez_ANOVA4<-ezANOVA(Data_analysis_women, dv=Attractiveness_check2, wid=ID, between=Attractive_condition*Dominant_condition, detailed=TRUE, type = 3)
Ez_ANOVA4
```

```{r}
require(apa)
anova_apa(Ez_ANOVA1, es="ges", format = "rmarkdown")
anova_apa(Ez_ANOVA2, es="ges", format = "rmarkdown")
anova_apa(Ez_ANOVA3, es="ges", format = "rmarkdown")
anova_apa(Ez_ANOVA4, es="ges", format = "rmarkdown")
```

```{r}
summary_attractive_men <- Data_analysis_men  %>% # "Start with the data set
  group_by(Attractive_condition) %>% # Then group by IV
  summarize(N = length(Attractiveness_check1), # Then summarize each group, these are complete so we can use same N
            Mean_att1 = mean(Attractiveness_check1),
            SD_att1 = sd(Attractiveness_check1),
            SE_att1 = SD_att1/sqrt(N), # Then summarize each group, these are complete so we can use same N
            Mean_att2 = mean(Attractiveness_check2),
            SD_att2 = sd(Attractiveness_check2),
            SE_att2 = SD_att2/sqrt(N)) 
summary_attractive_men

summary_attractive_women <- Data_analysis_women  %>% # "Start with the data set
  group_by(Attractive_condition) %>% # Then group by IV
  summarize(N = length(Attractiveness_check1), # Then summarize each group, these are complete so we can use same N
            Mean_att1 = mean(Attractiveness_check1),
            SD_att1 = sd(Attractiveness_check1),
            SE_att1 = SD_att1/sqrt(N), # Then summarize each group, these are complete so we can use same N
            Mean_att2 = mean(Attractiveness_check2),
            SD_att2 = sd(Attractiveness_check2),
            SE_att2 = SD_att2/sqrt(N)) 
summary_attractive_women

```

MANOVA for dominance (note no checks for assumption tests).

```{r}
Manovamodel_men <- manova(cbind(Assertiveness,`Self-confidence`,Extroverted,Influential,Socially_competent,Good_judge_of_character) ~ Dominant_condition, data = Data_analysis_men)
summary(Manovamodel_men)
summary(Manovamodel_men, test="Roy")
summary(Manovamodel_men, test="Wilks")
summary(Manovamodel_men, test="Hotelling-Lawley")
summary.aov(Manovamodel_men)
```

Note that there were 3 women who did not complete all items.

```{r}
Manovamodel_women <- manova(cbind(Assertiveness,`Self-confidence`,Extroverted,Influential,Socially_competent,Good_judge_of_character) ~ Dominant_condition, data = Data_analysis_women)
summary(Manovamodel_women)
summary(Manovamodel_women, test="Roy")
summary(Manovamodel_women, test="Wilks")
summary(Manovamodel_women, test="Hotelling-Lawley")
summary.aov(Manovamodel_women)
```

## Hypothesis tests

```{r}
Ez_ANOVA_jealousy<-ezANOVA(Data_analysis, dv=Jealousy, wid=ID, between=.(Attractive_condition,Dominant_condition,Gender), detailed=TRUE, type=3)
Ez_ANOVA_jealousy
anova_apa(Ez_ANOVA_jealousy, es="ges", format = "rmarkdown")
```

Same conclusion.

```{r}
require(dplyr)
Data_analysis_covar<- Data_analysis %>% filter(!is.na(Mate_value))
Ez_ANOVA_jealousy_covar<-ezANOVA(Data_analysis_covar, dv=Jealousy, wid=ID, between=.(Attractive_condition,Dominant_condition,Gender), between_covariates = Mate_value, detailed=TRUE, type=3)
Ez_ANOVA_jealousy_covar
anova_apa(Ez_ANOVA_jealousy_covar, es="ges", format = "rmarkdown")
```


```{r}
Ez_ANOVA_jealousy_men<-ezANOVA(Data_analysis_men, dv=Jealousy, wid=ID, between=Attractive_condition*Dominant_condition, detailed=TRUE, type=3)
Ez_ANOVA_jealousy_men
Ez_ANOVA_jealousy_women<-ezANOVA(Data_analysis_women, dv=Jealousy, wid=ID, between=Attractive_condition*Dominant_condition, detailed=TRUE, type=3)
Ez_ANOVA_jealousy_women
anova_apa(Ez_ANOVA_jealousy_men, es="ges", format = "rmarkdown")
anova_apa(Ez_ANOVA_jealousy_women, es="ges", format = "rmarkdown")
```

Means and SD.

```{r}
summary_jealousy_attractiveness_men <- Data_analysis_men  %>% # "Start with the data set
  group_by(Attractive_condition) %>% # Then group by IV
  summarize(N = length(Jealousy), # Then summarize each group, these are complete so we can use same N
            Mean_jeal = mean(Jealousy),
            SD_jeal = sd(Jealousy),
            SE_jeal = SD_jeal/sqrt(N)) # Then summarize each group, these are complete so we can use same N
summary_jealousy_attractiveness_men

summary_jealousy_attractiveness_women <- Data_analysis_women  %>% # "Start with the data set
  group_by(Attractive_condition) %>% # Then group by IV
  summarize(N = length(Jealousy), # Then summarize each group, these are complete so we can use same N
            Mean_jeal = mean(Jealousy),
            SD_jeal = sd(Jealousy),
            SE_jeal = SD_jeal/sqrt(N)) # Then summarize each group, these are complete so we can use same N
summary_jealousy_attractiveness_women
```

```{r}
summary_jealousy_dominant_men <- Data_analysis_men  %>% # "Start with the data set
  group_by(Dominant_condition) %>% # Then group by IV
  summarize(N = length(Jealousy), # Then summarize each group, these are complete so we can use same N
            Mean_jeal = mean(Jealousy),
            SD_jeal = sd(Jealousy),
            SE_jeal = SD_jeal/sqrt(N)) # Then summarize each group, these are complete so we can use same N
summary_jealousy_dominant_men

summary_jealousy_dominant_women <- Data_analysis_women  %>% # "Start with the data set
  group_by(Dominant_condition) %>% # Then group by IV
  summarize(N = length(Jealousy), # Then summarize each group, these are complete so we can use same N
            Mean_jeal = mean(Jealousy),
            SD_jeal = sd(Jealousy),
            SE_jeal = SD_jeal/sqrt(N)) # Then summarize each group, these are complete so we can use same N
summary_jealousy_dominant_women
```

## Figures

Men.

```{r}
require(ggplot2)
require(ggthemes)
require(scales)
graph_data_men <- describeBy(Data_analysis_men$Jealousy,list(as.factor(Data_analysis_men$Attractive_condition),as.factor(Data_analysis_men$Dominant_condition)), mat=TRUE,digits=2)

graph_data_women <- describeBy(Data_analysis_women$Jealousy,list(as.factor(Data_analysis_women$Attractive_condition),as.factor(Data_analysis_women$Dominant_condition)), mat=TRUE,digits=2)

names(graph_data_men)[names(graph_data_men) == 'group1'] = 'Attractiveness'
names(graph_data_men)[names(graph_data_men) == 'group2'] = 'Dominance'  
names(graph_data_women)[names(graph_data_women) == 'group1'] = 'Attractiveness'
names(graph_data_women)[names(graph_data_women) == 'group2'] = 'Dominance'  

limits = aes(ymax = mean + sd, ymin=mean - sd)
dodge = position_dodge(width=0.9)
graph_men_bar<-ggplot(graph_data_men, aes(x = Attractiveness, y = mean, fill = Dominance))+
  geom_bar(stat='identity', position=dodge)+
  geom_errorbar(limits, position=dodge, width=0.25) + xlab("Attractiveness condition")+ ylab("Mean Jealousy") + labs(fill="Dominance condition") + theme_tufte(10) + scale_fill_grey(start=.4) + coord_cartesian(ylim=c(1,5))
graph_men_bar
# Reference set
reference_men_mean<-c(3.15,3,3.39,2.44)
reference_men_SD<-c(1.16,1.25,.85,.98)
Attractiveness<-c("Attractive","Attractive","Not Attractive", "Not Attractive")
Dominance<-c("Dominant","Not Dominant","Dominant", "Not Dominant")
reference_men<-cbind.data.frame(reference_men_mean,reference_men_SD,Attractiveness,Dominance)
limits = aes(ymax = reference_men_mean + reference_men_SD, ymin=reference_men_mean - reference_men_SD)
dodge = position_dodge(width=0.9)

graph_men_reference<-ggplot(reference_men, aes(x = Attractiveness, y = reference_men_mean, fill = Dominance))+
  geom_bar(stat='identity', position=dodge)+ 
  geom_errorbar(limits, position=dodge, width=0.25) + xlab("Attractiveness condition")+ ylab("Mean Jealousy") + labs(fill="Dominance condition") + theme_tufte(10) + scale_fill_grey(start=.4) + coord_cartesian(ylim=c(1,5))
graph_men_reference
require(cowplot)
plot_grid(graph_men_bar, graph_men_reference, labels = c("A","B"), hjust = -8, label_size = 8,  ncol = 1, align = 'v')
ggsave("barplot_men.png")
ggsave("barplot_men.pdf")
```

Women

```{r}
require(ggplot2)
require(ggthemes)
require(scales)
graph_data_women <- describeBy(Data_analysis_women$Jealousy,list(as.factor(Data_analysis_women$Attractive_condition),as.factor(Data_analysis_women$Dominant_condition)), mat=TRUE,digits=2)

graph_data_women <- describeBy(Data_analysis_women$Jealousy,list(as.factor(Data_analysis_women$Attractive_condition),as.factor(Data_analysis_women$Dominant_condition)), mat=TRUE,digits=2)

names(graph_data_women)[names(graph_data_women) == 'group1'] = 'Attractiveness'
names(graph_data_women)[names(graph_data_women) == 'group2'] = 'Dominance'  
names(graph_data_women)[names(graph_data_women) == 'group1'] = 'Attractiveness'
names(graph_data_women)[names(graph_data_women) == 'group2'] = 'Dominance'  

limits = aes(ymax = mean + sd, ymin=mean - sd)
dodge = position_dodge(width=0.9)
graph_women_bar<-ggplot(graph_data_women, aes(x = Attractiveness, y = mean, fill = Dominance))+
  geom_bar(stat='identity', position=dodge)+
  geom_errorbar(limits, position=dodge, width=0.25) + xlab("Attractiveness condition")+ ylab("Mean Jealousy") + labs(fill="Dominance condition") + theme_tufte(10) + scale_fill_grey(start=.4) + coord_cartesian(ylim=c(1,5))
graph_women_bar
# Reference set
reference_women_mean<-c(3.62,3.48,2.47,2.83)
reference_women_SD<-c(1.12,1.12,1.07,1.34)
Attractiveness<-c("Attractive","Attractive","Not Attractive", "Not Attractive")
Dominance<-c("Dominant","Not Dominant","Dominant", "Not Dominant")
reference_women<-cbind.data.frame(reference_women_mean,reference_women_SD,Attractiveness,Dominance)
limits = aes(ymax = reference_women_mean + reference_women_SD, ymin=reference_women_mean - reference_women_SD)
dodge = position_dodge(width=0.9)

graph_women_reference<-ggplot(reference_women, aes(x = Attractiveness, y = reference_women_mean, fill = Dominance))+
  geom_bar(stat='identity', position=dodge)+ 
  geom_errorbar(limits, position=dodge, width=0.25) + xlab("Attractiveness condition")+ ylab("Mean Jealousy") + labs(fill="Dominance condition") + theme_tufte(10) + scale_fill_grey(start=.4) + coord_cartesian(ylim=c(1,5))
graph_women_reference
require(cowplot)
plot_grid(graph_women_bar, graph_women_reference, labels = c("A","B"), hjust = -8, label_size = 8,  ncol = 1, align = 'v')
ggsave("barplot_women.png")
ggsave("barplot_women.pdf")
```


### Violin plot

This violin plot looks a bit hideous. That is why we opted for the histogram.

```{r}

Data_analysis$Gender<-as.factor(Data_analysis$Gender)
levels(Data_analysis$Gender) <- c("Men", "Women")
dodge <- position_dodge(width = 0.7)
violinplot<-ggplot(Data_analysis, aes(x = Attractive_condition, y = Jealousy, fill=Dominant_condition)) + geom_violin(position=dodge) + geom_boxplot(position=dodge,width = 0.1, outlier.colour=NA) + xlab("Attractiveness condition")+ ylab("Jealousy") + labs(fill="Dominance condition") + theme(legend.position = "top") + facet_grid(~Gender) + scale_fill_grey(start=.4) + theme_tufte(12)
violinplot
ggsave("violinplot.png", width= 200, height=200, units="mm")
```

```{r}
histogram_men<-ggplot(Data_analysis_men, aes(x=Jealousy)) 
histogram_men <- histogram_men + geom_histogram(binwidth=.5, colour="black", fill="white") + facet_grid(Attractive_condition~Dominant_condition) + theme_tufte(7.5)

histogram_women<-ggplot(Data_analysis_women, aes(x=Jealousy)) 
histogram_women <- histogram_women + geom_histogram(binwidth=.5, colour="black", fill="white") + facet_grid(Attractive_condition~Dominant_condition) + theme_tufte(7.5)

plot_grid(histogram_men, histogram_women, labels = c("Men (N=114)","Women (N=225)"), label_size = 7,  ncol = 1, align = 'v')
ggsave("histogram.png")
ggsave("histogram.pdf")
```



## Additional analyses.

```{r}
require(coin)
require(BayesFactor)
Data_analysis$Attractive_condition<-as.factor(Data_analysis$Attractive_condition)
Data_analysis$Dominant_condition<-as.factor(Data_analysis$Dominant_condition)
Data_analysis$Gender<-as.factor(Data_analysis$Gender)
bf_jealousy <- anovaBF(Jealousy ~ Attractive_condition*Dominant_condition*Gender, data=as.data.frame(Data_analysis))
bf_jealousy
1/bf_jealousy 
independence_test(Jealousy ~ Attractive_condition*Dominant_condition*Gender, data=Data_analysis)
```

```{r}
require(broom)
result_broom<-tidy(bf_jealousy)
write.csv(result_broom, "Bayes_1.csv")
```


The independence test is not significant (but _p_ =.06 in independence test for men). 

```{r}
require(coin)
require(BayesFactor)
Data_analysis_men$Attractive_condition<-as.factor(Data_analysis_men$Attractive_condition)
Data_analysis_men$Dominant_condition<-as.factor(Data_analysis_men$Dominant_condition)
bf_jealousy_men <- anovaBF(Jealousy ~ Attractive_condition*Dominant_condition, data=as.data.frame(Data_analysis_men))
bf_jealousy_men
1/bf_jealousy_men 
independence_test(Jealousy ~ Attractive_condition*Dominant_condition, data=Data_analysis_men)
Data_analysis_women$Attractive_condition<-as.factor(Data_analysis_women$Attractive_condition)
Data_analysis_women$Dominant_condition<-as.factor(Data_analysis_women$Dominant_condition)
bf_jealousy_women <- anovaBF(Jealousy ~ Attractive_condition*Dominant_condition, data=as.data.frame(Data_analysis_women))
bf_jealousy_women
1/bf_jealousy_women # 
independence_test(Jealousy ~ Attractive_condition*Dominant_condition, data=Data_analysis_women)
```

```{r}
require(broom)
result_broom<-tidy(bf_jealousy_men)
write.csv(result_broom, "Bayes_2.csv")
result_broom2<-tidy(bf_jealousy_women)
write.csv(result_broom2, "Bayes_3.csv")
```

## Bootstrapping.

Note that this will take some time. We cannot specify type of error here.

```{r}
ezBoot1<-ezBoot(Data_analysis_men, dv=Jealousy, wid=ID, between=Attractive_condition*Dominant_condition, resample_within = F, iterations = 1e3)
ezBoot2<-ezBoot(Data_analysis_women, dv=Jealousy, wid=ID, between=Attractive_condition*Dominant_condition, resample_within = F, iterations = 1e3)
```

Plot for bootstrap.

```{r}
p<-ezPlot2(pred=ezBoot1, x= Attractive_condition,split=Dominant_condition)
print(p)
p2<-ezPlot2(pred=ezBoot2, x= Attractive_condition,split=Dominant_condition)
print(p2)
```


## Robustness check for site of collection.

Some of the lower level interaction effects significant but crucially no support for a significant three-way interaction.

```{r}
Ez_ANOVA_jealousy_men_check<-ezANOVA(Data_analysis_men, dv=Jealousy, wid=ID, between=.(Attractive_condition,Dominant_condition,Sample), detailed=TRUE, type=3)
Ez_ANOVA_jealousy_men_check
Ez_ANOVA_jealousy_women_check<-ezANOVA(Data_analysis_women, dv=Jealousy, wid=ID, between=.(Attractive_condition,Dominant_condition,Sample), detailed=TRUE, type=3)
Ez_ANOVA_jealousy_women_check
anova_apa(Ez_ANOVA_jealousy_men_check, es="ges", format = "rmarkdown")
anova_apa(Ez_ANOVA_jealousy_women_check, es="ges", format = "rmarkdown")
```

# Study 2

Note that this overrides some of the code, as it is based on the same code as study 1

## Data Wrangling

Importing the datasets for entire study. These are as they were on Qualtrics, with the exception of the removal of IP addresses, 'preview' completions, and personal codes allowing withdrawal

```{r}
require(dplyr)
require(skimr)
require(haven)
Data_online<-read_spss("Study2-Online.sav")
Data_field<-read_spss("Study2-Field.sav")
```
 
Q98 is the last question, therefore this indicates completion.

```{r}
Data_online <- Data_online %>% filter(!is.na(Q98))
Data_field <- Data_field %>% filter(!is.na(Q98))
```

Only heterosexual participants included.

```{r}
Data_online<-Data_online %>% filter(Q6==1)
Data_field <- Data_field %>% filter(Q6==1)
```

Age for descriptives.

```{r}
Age<-c(Data_online$Q5,Data_field$Q5)
mean(Age)
sd(Age)
```

Gender for descriptives.

```{r}
Gender<-c(Data_online$Q4,Data_field$Q4)
table(Gender)
prop.table(table(Gender))
```

Student and romantic relationship for descriptives

```{r}
Student<-c(Data_online$Q8,Data_field$Q8)
table(Student)
prop.table(table(Student))
Romantic<-c(Data_online$Q7,Data_field$Q7)
table(Romantic)
prop.table(table(Romantic))
``` 

## Subset for analysis

```{r}
Data_analysis1<- Data_online %>% select(Q4,Q23:Q37,Q39,Q40,Q41,Q42,Q43,Q44,FL_21_DO_Scenario5_attractiveandnotdominantfemale,FL_21_DO_Scenario7_unattractiveanddominantfemale,FL_21_DO_Scenario6_attractiveanddominantfemale,FL_21_DO_Scenario8_unattractiveandnotdominantfemale,FL_17_DO_Scenario_attractiveandnon_dominantmale,FL_17_DO_Scenario3_dominantandunattractivemale,FL_17_DO_Scenario1_attractiveanddominantmale,FL_17_DO_Scenario4_NotDominantandUnattractivemale, Q93:Q98)
names(Data_analysis1)<-c("Gender","Suspicious","Bertrayed","Worried","Distrustful","Jealousy","Rejected","Hurt","Anxious","Angry", "Threatened","Sad","Upset","Attractiveness_check1","Attractiveness_check2","Assertiveness","Self-confidence","Extroverted","Influential","Socially_competent","Good_judge_of_character","Attractive_not_dominant_woman","Unattractive_dominant_woman","Attractive_dominant_woman","Unattractive_not_dominant_woman","Attractive_not_dominant_man","Unattractive_dominant_man","Attractive_dominant_man","Unattractive_not_dominant_man","Mate_value1","Mate_value2", "Mate_value3","Mate_value4", "Mate_value5", "Mate_value6")
Data_analysis1$Sample<-rep("Online",nrow(Data_analysis1))
# For some reason qualtrics exports.The label here but not elsewhere Q34.
Data_analysis2<- Data_field %>% select(Q4,Q23:Q34, Q36:Q37,Q39,Q40,Q41,Q42,Q43,Q44,FL_21_DO_Scenario5_attractiveandnotdominantfemale,FL_21_DO_Scenario7_unattractiveanddominantfemale,FL_21_DO_Scenario6_attractiveanddominantfemale,FL_21_DO_Scenario8_unattractiveandnotdominantfemale,FL_17_DO_Scenario_attractiveandnon_dominantmale,FL_17_DO_Scenario3_dominantandunattractivemale,FL_17_DO_Scenario1_attractiveanddominantmale,FL_17_DO_Scenario4_NotDominantandUnattractivemale, Q93:Q98)
names(Data_analysis2)<-c("Gender","Suspicious","Bertrayed","Worried","Distrustful","Jealousy","Rejected","Hurt","Anxious","Angry", "Threatened","Sad","Upset","Attractiveness_check1","Attractiveness_check2","Assertiveness","Self-confidence","Extroverted","Influential","Socially_competent","Good_judge_of_character","Attractive_not_dominant_woman","Unattractive_dominant_woman","Attractive_dominant_woman","Unattractive_not_dominant_woman","Attractive_not_dominant_man","Unattractive_dominant_man","Attractive_dominant_man","Unattractive_not_dominant_man", "Mate_value1","Mate_value2", "Mate_value3","Mate_value4", "Mate_value5", "Mate_value6")
Data_analysis2$Sample<-rep("Field",nrow(Data_analysis2))
Data_analysis<-rbind(Data_analysis1,Data_analysis2)
```

## Recode to get the 2x2 condition variable. 

Using "case_when". Also generate ID

```{r}
Data_analysis<-Data_analysis %>% mutate(Attractive_condition=case_when(Attractive_not_dominant_woman == 1 | Attractive_dominant_woman == 1 | Attractive_not_dominant_man == 1 | Attractive_dominant_man == 1 ~ "Attractive", TRUE ~ "Not Attractive"), Dominant_condition=case_when(Attractive_dominant_woman == 1 | Unattractive_dominant_woman == 1 | Attractive_dominant_man == 1 | Unattractive_dominant_man == 1 ~ "Dominant", TRUE ~ "Not Dominant"), ID=1:nrow(Data_analysis))
```

## Cronbach's alpha.

```{r}
require(psych)
alpha<- Data_analysis %>% dplyr::select(Mate_value1:Mate_value6)
require(psych)
psych::alpha(as.data.frame(alpha))
```

Sum scale.

```{r}
Data_analysis<-Data_analysis %>% mutate(Mate_value= Mate_value1+Mate_value2+Mate_value3+Mate_value4+Mate_value5+Mate_value6)
```

There was no significant difference between the genders in mate value, therefore there is no value of including mate value as a covariate. Note that there is one missing value.

```{r}
t.test(Mate_value~Gender, data=Data_analysis)
```

```{r}
describeBy(Data_analysis$Mate_value, Data_analysis$Gender)
```


```{r}
library(lsr)
cohensD(Data_analysis$Mate_value~ Data_analysis$Gender)
```
```{r}
library(compute.es)
des(d=.2240383, n.1=178, n.2=277)
```

Similar to Dijkstra et al. 1998, there were no significant effects of conditons on mate value (but _p_=.09 for attractiveness). 

```{r}
t.test(Mate_value~Attractive_condition, data=Data_analysis)
t.test(Mate_value~Dominant_condition, data=Data_analysis)
```

## Manipulation checks.

Using the 'ez' package.

```{r}
require(dplyr)
Data_analysis_men<- Data_analysis %>% filter(Gender==1)
Data_analysis_women<- Data_analysis %>% filter(Gender==2)

```


```{r}
require(ez)
require(papaja)
Ez_ANOVA1<-ezANOVA(Data_analysis_men, dv=Attractiveness_check1, wid=ID, between=Attractive_condition*Dominant_condition, detailed=TRUE, type = 3)
Ez_ANOVA1
Ez_ANOVA2<-ezANOVA(Data_analysis_women, dv=Attractiveness_check1, wid=ID, between=Attractive_condition*Dominant_condition, detailed=TRUE, type = 3)
Ez_ANOVA2
Ez_ANOVA3<-ezANOVA(Data_analysis_men, dv=Attractiveness_check2, wid=ID, between=Attractive_condition*Dominant_condition, detailed=TRUE, type = 3)
Ez_ANOVA3
Ez_ANOVA4<-ezANOVA(Data_analysis_women, dv=Attractiveness_check2, wid=ID, between=Attractive_condition*Dominant_condition, detailed=TRUE, type = 3)
Ez_ANOVA4
```

```{r}
require(apa)
anova_apa(Ez_ANOVA1, es="ges", format = "rmarkdown")
anova_apa(Ez_ANOVA2, es="ges", format = "rmarkdown")
anova_apa(Ez_ANOVA3, es="ges", format = "rmarkdown")
anova_apa(Ez_ANOVA4, es="ges", format = "rmarkdown")
```

```{r}
summary_attractive_men <- Data_analysis_men  %>% # "Start with the data set
  group_by(Attractive_condition) %>% # Then group by IV
  summarize(N = length(Attractiveness_check1), # Then summarize each group, these are complete so we can use same N
            Mean_att1 = mean(Attractiveness_check1),
            SD_att1 = sd(Attractiveness_check1),
            SE_att1 = SD_att1/sqrt(N), # Then summarize each group, these are complete so we can use same N
            Mean_att2 = mean(Attractiveness_check2),
            SD_att2 = sd(Attractiveness_check2),
            SE_att2 = SD_att2/sqrt(N)) 
summary_attractive_men

summary_attractive_women <- Data_analysis_women  %>% # "Start with the data set
  group_by(Attractive_condition) %>% # Then group by IV
  summarize(N = length(Attractiveness_check1), # Then summarize each group, these are complete so we can use same N
            Mean_att1 = mean(Attractiveness_check1),
            SD_att1 = sd(Attractiveness_check1),
            SE_att1 = SD_att1/sqrt(N), # Then summarize each group, these are complete so we can use same N
            Mean_att2 = mean(Attractiveness_check2),
            SD_att2 = sd(Attractiveness_check2),
            SE_att2 = SD_att2/sqrt(N)) 
summary_attractive_women

```

MANOVA for dominance (note no checks for assumption tests).

```{r}
Manovamodel_men <- manova(cbind(Assertiveness,`Self-confidence`,Extroverted,Influential,Socially_competent,Good_judge_of_character) ~ Dominant_condition, data = Data_analysis_men)
summary(Manovamodel_men)
summary(Manovamodel_men, test="Roy")
summary(Manovamodel_men, test="Wilks")
summary(Manovamodel_men, test="Hotelling-Lawley")
summary.aov(Manovamodel_men)
```

Women.

```{r}
Manovamodel_women <- manova(cbind(Assertiveness,`Self-confidence`,Extroverted,Influential,Socially_competent,Good_judge_of_character) ~ Dominant_condition, data = Data_analysis_women)
summary(Manovamodel_women)
summary(Manovamodel_women, test="Roy")
summary(Manovamodel_women, test="Wilks")
summary(Manovamodel_women, test="Hotelling-Lawley")
summary.aov(Manovamodel_women)
```

## Hypothesis tests

```{r}
Ez_ANOVA_jealousy<-ezANOVA(Data_analysis, dv=Jealousy, wid=ID, between=.(Attractive_condition,Dominant_condition,Gender), detailed=TRUE, type=3)
Ez_ANOVA_jealousy
anova_apa(Ez_ANOVA_jealousy, es="ges", format = "rmarkdown")
```

Same conclusion.

```{r}
require(dplyr)
Data_analysis_covar<- Data_analysis %>% filter(!is.na(Mate_value))
Ez_ANOVA_jealousy_covar<-ezANOVA(Data_analysis_covar, dv=Jealousy, wid=ID, between=.(Attractive_condition,Dominant_condition,Gender), between_covariates = Mate_value, detailed=TRUE, type=3)
Ez_ANOVA_jealousy_covar
anova_apa(Ez_ANOVA_jealousy_covar, es="ges", format = "rmarkdown")
```


```{r}
Ez_ANOVA_jealousy_men<-ezANOVA(Data_analysis_men, dv=Jealousy, wid=ID, between=Attractive_condition*Dominant_condition, detailed=TRUE, type=3)
Ez_ANOVA_jealousy_men
Ez_ANOVA_jealousy_women<-ezANOVA(Data_analysis_women, dv=Jealousy, wid=ID, between=Attractive_condition*Dominant_condition, detailed=TRUE, type=3)
Ez_ANOVA_jealousy_women
anova_apa(Ez_ANOVA_jealousy_men, es="ges", format = "rmarkdown")
anova_apa(Ez_ANOVA_jealousy_women, es="ges", format = "rmarkdown")
```

Means and SD.

```{r}
summary_jealousy_attractiveness_men <- Data_analysis_men  %>% # "Start with the data set
  group_by(Attractive_condition) %>% # Then group by IV
  summarize(N = length(Jealousy), # Then summarize each group, these are complete so we can use same N
            Mean_jeal = mean(Jealousy),
            SD_jeal = sd(Jealousy),
            SE_jeal = SD_jeal/sqrt(N)) # Then summarize each group, these are complete so we can use same N
summary_jealousy_attractiveness_men

summary_jealousy_attractiveness_women <- Data_analysis_women  %>% # "Start with the data set
  group_by(Attractive_condition) %>% # Then group by IV
  summarize(N = length(Jealousy), # Then summarize each group, these are complete so we can use same N
            Mean_jeal = mean(Jealousy),
            SD_jeal = sd(Jealousy),
            SE_jeal = SD_jeal/sqrt(N)) # Then summarize each group, these are complete so we can use same N
summary_jealousy_attractiveness_women
```

```{r}
summary_jealousy_dominant_men <- Data_analysis_men  %>% # "Start with the data set
  group_by(Dominant_condition) %>% # Then group by IV
  summarize(N = length(Jealousy), # Then summarize each group, these are complete so we can use same N
            Mean_jeal = mean(Jealousy),
            SD_jeal = sd(Jealousy),
            SE_jeal = SD_jeal/sqrt(N)) # Then summarize each group, these are complete so we can use same N
summary_jealousy_dominant_men

summary_jealousy_dominant_women <- Data_analysis_women  %>% # "Start with the data set
  group_by(Dominant_condition) %>% # Then group by IV
  summarize(N = length(Jealousy), # Then summarize each group, these are complete so we can use same N
            Mean_jeal = mean(Jealousy),
            SD_jeal = sd(Jealousy),
            SE_jeal = SD_jeal/sqrt(N)) # Then summarize each group, these are complete so we can use same N
summary_jealousy_dominant_women
```

## Figures

Men.

```{r}
require(ggplot2)
require(ggthemes)
require(scales)
graph_data_men <- describeBy(Data_analysis_men$Jealousy,list(as.factor(Data_analysis_men$Attractive_condition),as.factor(Data_analysis_men$Dominant_condition)), mat=TRUE,digits=2)

graph_data_women <- describeBy(Data_analysis_women$Jealousy,list(as.factor(Data_analysis_women$Attractive_condition),as.factor(Data_analysis_women$Dominant_condition)), mat=TRUE,digits=2)

names(graph_data_men)[names(graph_data_men) == 'group1'] = 'Attractiveness'
names(graph_data_men)[names(graph_data_men) == 'group2'] = 'Dominance'  
names(graph_data_women)[names(graph_data_women) == 'group1'] = 'Attractiveness'
names(graph_data_women)[names(graph_data_women) == 'group2'] = 'Dominance'  

limits = aes(ymax = mean + sd, ymin=mean - sd)
dodge = position_dodge(width=0.9)
graph_men_bar<-ggplot(graph_data_men, aes(x = Attractiveness, y = mean, fill = Dominance))+
  geom_bar(stat='identity', position=dodge)+
  geom_errorbar(limits, position=dodge, width=0.25) + xlab("Attractiveness condition")+ ylab("Mean Jealousy") + labs(fill="Dominance condition") + theme_tufte(10) + scale_fill_grey(start=.4) + coord_cartesian(ylim=c(1,5))
graph_men_bar
# Reference set
reference_men_mean<-c(3.15,3,3.39,2.44)
reference_men_SD<-c(1.16,1.25,.85,.98)
Attractiveness<-c("Attractive","Attractive","Not Attractive", "Not Attractive")
Dominance<-c("Dominant","Not Dominant","Dominant", "Not Dominant")
reference_men<-cbind.data.frame(reference_men_mean,reference_men_SD,Attractiveness,Dominance)
limits = aes(ymax = reference_men_mean + reference_men_SD, ymin=reference_men_mean - reference_men_SD)
dodge = position_dodge(width=0.9)

graph_men_reference<-ggplot(reference_men, aes(x = Attractiveness, y = reference_men_mean, fill = Dominance))+
  geom_bar(stat='identity', position=dodge)+ 
  geom_errorbar(limits, position=dodge, width=0.25) + xlab("Attractiveness condition")+ ylab("Mean Jealousy") + labs(fill="Dominance condition") + theme_tufte(10) + scale_fill_grey(start=.4) + coord_cartesian(ylim=c(1,5))
graph_men_reference
require(cowplot)
plot_grid(graph_men_bar, graph_men_reference, labels = c("A","B"), hjust = -8, label_size = 8,  ncol = 1, align = 'v')
ggsave("barplot_men_2.png")
ggsave("barplot_men_2.pdf")
```

Women

```{r}
require(ggplot2)
require(ggthemes)
require(scales)
graph_data_women <- describeBy(Data_analysis_women$Jealousy,list(as.factor(Data_analysis_women$Attractive_condition),as.factor(Data_analysis_women$Dominant_condition)), mat=TRUE,digits=2)

graph_data_women <- describeBy(Data_analysis_women$Jealousy,list(as.factor(Data_analysis_women$Attractive_condition),as.factor(Data_analysis_women$Dominant_condition)), mat=TRUE,digits=2)

names(graph_data_women)[names(graph_data_women) == 'group1'] = 'Attractiveness'
names(graph_data_women)[names(graph_data_women) == 'group2'] = 'Dominance'  
names(graph_data_women)[names(graph_data_women) == 'group1'] = 'Attractiveness'
names(graph_data_women)[names(graph_data_women) == 'group2'] = 'Dominance'  

limits = aes(ymax = mean + sd, ymin=mean - sd)
dodge = position_dodge(width=0.9)
graph_women_bar<-ggplot(graph_data_women, aes(x = Attractiveness, y = mean, fill = Dominance))+
  geom_bar(stat='identity', position=dodge)+
  geom_errorbar(limits, position=dodge, width=0.25) + xlab("Attractiveness condition")+ ylab("Mean Jealousy") + labs(fill="Dominance condition") + theme_tufte(10) + scale_fill_grey(start=.4) + coord_cartesian(ylim=c(1,5))
graph_women_bar
# Reference set
reference_women_mean<-c(3.62,3.48,2.47,2.83)
reference_women_SD<-c(1.12,1.12,1.07,1.34)
Attractiveness<-c("Attractive","Attractive","Not Attractive", "Not Attractive")
Dominance<-c("Dominant","Not Dominant","Dominant", "Not Dominant")
reference_women<-cbind.data.frame(reference_women_mean,reference_women_SD,Attractiveness,Dominance)
limits = aes(ymax = reference_women_mean + reference_women_SD, ymin=reference_women_mean - reference_women_SD)
dodge = position_dodge(width=0.9)

graph_women_reference<-ggplot(reference_women, aes(x = Attractiveness, y = reference_women_mean, fill = Dominance))+
  geom_bar(stat='identity', position=dodge)+ 
  geom_errorbar(limits, position=dodge, width=0.25) + xlab("Attractiveness condition")+ ylab("Mean Jealousy") + labs(fill="Dominance condition") + theme_tufte(10) + scale_fill_grey(start=.4) + coord_cartesian(ylim=c(1,5))
graph_women_reference
require(cowplot)
plot_grid(graph_women_bar, graph_women_reference, labels = c("A","B"), hjust = -8, label_size = 8,  ncol = 1, align = 'v')
ggsave("barplot_women_2.png")
ggsave("barplot_women_2.pdf")
```

### Violin plot

This violin plot looks a bit hideous. That is why we opted for the histogram.

```{r}

Data_analysis$Gender<-as.factor(Data_analysis$Gender)
levels(Data_analysis$Gender) <- c("Men", "Women")
dodge <- position_dodge(width = 0.7)
violinplot<-ggplot(Data_analysis, aes(x = Attractive_condition, y = Jealousy, fill=Dominant_condition)) + geom_violin(position=dodge) + geom_boxplot(position=dodge,width = 0.1, outlier.colour=NA) + xlab("Attractiveness condition")+ ylab("Jealousy") + labs(fill="Dominance condition") + theme(legend.position = "top") + facet_grid(~Gender) + scale_fill_grey(start=.4) + theme_tufte(12)
violinplot
ggsave("violinplot_2.png", width= 200, height=200, units="mm")
```

```{r}
histogram_men<-ggplot(Data_analysis_men, aes(x=Jealousy)) 
histogram_men <- histogram_men + geom_histogram(binwidth=.5, colour="black", fill="white") + facet_grid(Attractive_condition~Dominant_condition) + theme_tufte(7.5)

histogram_women<-ggplot(Data_analysis_women, aes(x=Jealousy)) 
histogram_women <- histogram_women + geom_histogram(binwidth=.5, colour="black", fill="white") + facet_grid(Attractive_condition~Dominant_condition) + theme_tufte(7.5)

plot_grid(histogram_men, histogram_women, labels = c("Men (N=178)","Women (N=278)"), label_size = 7,  ncol = 1, align = 'v')
ggsave("histogram_2.png")
ggsave("histogram_2.pdf")
```

### Additional analyses

independence test suggests no effect

```{r}
require(coin)
require(BayesFactor)
Data_analysis$Attractive_condition<-as.factor(Data_analysis$Attractive_condition)
Data_analysis$Dominant_condition<-as.factor(Data_analysis$Dominant_condition)
Data_analysis$Gender<-as.factor(Data_analysis$Gender)
bf_jealousy <- anovaBF(Jealousy ~ Attractive_condition*Dominant_condition*Gender, data=as.data.frame(Data_analysis))
bf_jealousy
1/bf_jealousy 
independence_test(Jealousy ~ Attractive_condition*Dominant_condition*Gender, data=Data_analysis)
```


```{r}
require(broom)
result_broom<-tidy(bf_jealousy)
write.csv(result_broom, "Bayes_4.csv")
```



```{r}
require(broom)
result_broom<-tidy(bf_jealousy)
write.csv(result_broom, "Bayes_1.csv")
```



```{r}
require(coin)
require(BayesFactor)
Data_analysis_men$Attractive_condition<-as.factor(Data_analysis_men$Attractive_condition)
Data_analysis_men$Dominant_condition<-as.factor(Data_analysis_men$Dominant_condition)
bf_jealousy_men <- anovaBF(Jealousy ~ Attractive_condition*Dominant_condition, data=as.data.frame(Data_analysis_men))
bf_jealousy_men
1/bf_jealousy_men 
independence_test(Jealousy ~ Attractive_condition*Dominant_condition, data=Data_analysis_men)
Data_analysis_women$Attractive_condition<-as.factor(Data_analysis_women$Attractive_condition)
Data_analysis_women$Dominant_condition<-as.factor(Data_analysis_women$Dominant_condition)
bf_jealousy_women <- anovaBF(Jealousy ~ Attractive_condition*Dominant_condition, data=as.data.frame(Data_analysis_women))
bf_jealousy_women
1/bf_jealousy_women # 
independence_test(Jealousy ~ Attractive_condition*Dominant_condition, data=Data_analysis_women)
```

```{r}
require(broom)
result_broom<-tidy(bf_jealousy_men)
write.csv(result_broom, "Bayes_5.csv")
result_broom2<-tidy(bf_jealousy_women)
write.csv(result_broom2, "Bayes_6.csv")
```

# Meta-analysis.
We can use the guidance from http://www.stat-help.com/spreadsheets.html to convert everything to a common effect 'r'. Following the recommendation we can take square root of $\eta^2_p$ to obtain Pearson r. We use the sample sizes as N.

## attractiveness

### Build up a data frame

```{r}
require(esc)
require(metafor)
r_original_att<-sqrt(.0332) # Partial eta squared to r.
r_att1<-pearsons_r(eta=0.0194012518)
r_att2<-pearsons_r(eta=0.0027411646)
N_original<-152
N_1<-339
N_2<-456
r_i_attract<-c(r_original_att,r_att1,r_att2)
N_i<-c(N_original,N_1,N_2)
Labels<-c("Dijkstra & Buunk 1998: attractiveness*gender (N=152)", "Study 1: attractiveness*gender (N=339)", "Study 2: attractiveness*gender (N=456)")
correlations_1<-cbind.data.frame(r_i_attract, N_i, Labels)
```
Actual analysis
```{r}
require(metafor)
eszcor <- escalc(measure="ZCOR", ri=r_i_attract, ni=N_i, data=correlations_1)
REmodel_attract <-rma(yi=yi, vi=vi, data=eszcor, method="REML", slab=Labels)
REmodel_attract
postscript("forest1.eps",  horizontal = FALSE, onefile = FALSE, paper = "special", height = 12, width = 12)
par(mar=c(5,4,0,6))
forest(REmodel_attract)
dev.off()
```


```{r}
require(bayesmeta)
ma01 <- bayesmeta(y= eszcor[,"yi"], sigma= sqrt(eszcor[,"vi"]), mu.prior.mean = 0, mu.prior.sd = 4,
 tau.prior = function(t){dhalfnormal(t,scale=0.5)})
ma01
forestplot(ma01)
ma01$bayesfactor[1] # Bayes factor
ma01$bayesfactor[2] # minimum bayes factor
```
## Dominance

```{r}
require(esc)
require(metafor)
r_original_dom<-sqrt(.02646373) # Partial eta squared to r.
r_dom1<-pearsons_r(eta=0.0043368855)
r_dom2<-pearsons_r(eta=0.0003447257)
N_original<-152
N_1<-339
N_2<-456
r_i_dom<-c(r_original_dom,r_dom1,r_dom2)
N_i<-c(N_original,N_1,N_2)
Labels2<-c("Dijkstra & Buunk 1998: dominance*gender (N=152)", "Study 1: dominance*gender (N=339)", "Study 2: dominance*gender (N=456)")
correlations_2<-cbind.data.frame(r_i_dom, N_i, Labels2)
```

```{r}
require(metafor)
eszcor2 <- escalc(measure="ZCOR", ri=r_i_dom, ni=N_i, data=correlations_2)
REmodel_dom <-rma(yi=yi, vi=vi, data=eszcor2, method="REML", slab=Labels2)
REmodel_dom
postscript("forest2.eps",  horizontal = FALSE, onefile = FALSE, paper = "special", height = 12, width = 12)
par(mar=c(5,4,0,6))
forest(REmodel_dom)
dev.off()
```

```{r}
require(esc)
```


# Session info.

```{r}
sessionInfo()
```







